### 2024-04-01 outputs/paper/datasheet_template.qmd
Update datasheet_template.qmd

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: Chay Park
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- TBD
2. *How many instances are there in total (of each type, if appropriate)?*
	- TBD
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- TBD
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- TBD
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- TBD
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- TBD
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- TBD
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- TBD
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- TBD
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- TBD
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-04-01 outputs/paper/paper.qmd
Update paper.qmd

---
title: "Are we living in depressive society?"
subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"
author: Chay Park
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-01 outputs/paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Are we living in depressive society?"
+title: "Are we living in a depressive society?"
 subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"

### 2024-04-01 scripts/00-simulate_data.R
update

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Chay Park
+# Date: 2 April 2024
+# Contact: chay.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-04-02 scripts/00-simulate_data.R
Update scripts file and README

@@ -1,19 +1,77 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
+# Purpose: Simulates the scenario, creates the dataset, plots the data, runs the tests code based on the simulated data
 # Author: Chay Park
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Pre-install necessary packages 
 
 
 #### Workspace setup ####
+
+# Load necessary libraries
 library(tidyverse)
-# [...UPDATE THIS...]
+library(lubridate)
+library(testthat)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(123)  # For reproducibility
+data <- expand.grid(
+  Date = seq(ymd('2020-01-01'), ymd('2024-12-31'), by="1 month"),
+  AgeGroup = c('18-29', '30-39', '40-49', '50-59', '60-69', '70-79', '80+'),
+  RaceEthnicity = c('White', 'Black', 'Hispanic', 'Asian', 'Other'),
+  EducationLevel = c('Less than HS', 'HS Graduate', 'Some College', 'Bachelor’s', 'Graduate'),
+  Sex = c('Male', 'Female')
+)
 
+# Generate random anxiety and depression levels
+data$AnxietyLevel <- round(runif(nrow(data), 20, 80), 0)
+data$DepressionLevel <- round(runif(nrow(data), 20, 80), 0)
 
+# View the first few rows of the dataset
+head(data)
 
+# Aggregate data for plotting
+monthly_data <- data %>%
+  group_by(Date, AgeGroup) %>%
+  summarise(
+    AvgAnxiety = mean(AnxietyLevel),
+    AvgDepression = mean(DepressionLevel),
+    .groups = 'drop'  # To avoid grouping-related warnings in summarise
+  )
+
+# Test the structure of the dataset
+test_that("Data structure is correct", {
+  expect_true(all(c("Date", "AgeGroup", "RaceEthnicity", "EducationLevel", "Sex", "AnxietyLevel", "DepressionLevel") %in% names(data)))
+  expect_type(data$Date, "Date")
+  expect_type(data$AgeGroup, "factor")
+  expect_type(data$AnxietyLevel, "numeric")
+  expect_type(data$DepressionLevel, "numeric")
+})
+
[…]

### 2024-04-02 scripts/01-download_data.R

@@ -1,26 +1,20 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from online data source platform, data.cdc.gov
+# Author: Chay Park
+# Date: 2 April 2024
+# Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Stable internet connection, be able to connect to the Web browser
 
 
-#### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
+#### Procedure ####
+# Step 1) Type the following url 'data.cdc.gov' on your web browser
+# Step 2) Search "Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days"
+# Step 3) Make sure to check the data set is sort by Most Relevant
+# Step 4) Click a data set with a title "Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days"
+# Step 5) Double check the data is provided by NCHS/DHIS and the publisher is National Center for Health Statistics
+# Step 6) Click Export button on the top right to export dataset. Before downloading the data, make sure it's set to download file and export format is in CSV.
+# Step 7) Search "Lack of Social Connection" 
+# Step 8) Click the dataset and check the data is provided by NCHS/DHIS and the publisher is National Center for Health Statistics
+# Step 8) Download the dataset by exporting it in CSV format
          

### 2024-04-02 scripts/02-data_cleaning.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw plane data recorded by National Center for Health Statistics
+# Author: Chay Park
+# Date: 2 April 2024
+# Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Pre-install package called janitor
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-04-02 scripts/03-test_data.R

@@ -1,15 +1,14 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the codes on the cleaned dataset 
+# Author: Chay Park
+# Date: 2 April 2024
+# Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Pre-install necessary packages, tidyverse, lubridate, testthat
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####

### 2024-04-02 outputs/paper/paper.qmd
update

--- 2024-04-01 outputs/paper/paper.qmd
@@
 ---
-title: "Are we living in depressive society?"
+title: "Are we living in a depressive society?"
 subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"
 author: Chay Park
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Analyzing daata spanning from 2020 to 2024, we examine variatinos in anxiety or depressive disorders among different age groups, sex, race/ethnicity, and education level.
+Our analysis yncovers additional factors contributing to this trend.
+"
 format: pdf
@@
 You can and should cross-reference sections and sub-sections.
+The remainder of this paper is structured as follows. @sec-data....
 
-The remainder of this paper is structured as follows. @sec-data....
+Depression and anxiety are common symptoms of mental disorders in modern world.
+It could be light or serious.
+Someone could suffer it for longer period of time than the others, or someone could go through on a regular basis.
+It could be due to hormonal effect or circumstance that one confronting or even a weather can affect such level.
+!!According to ~ depression is ~ anxiety ~ !!
+It is not a country specific problem, but matters in the whole generation in global scale.
+
+Due to the Covid-19 global pandemic, many countries took a lockdown measure and the US was not the exceptional.
+The U.S.
+Census Bureau launched the Household Pulse Survey to produce data on the social and economic impacts of Covid-19 on American households in collaboration with five federal agencies.
+The Household Pulse Survey was designed to gauge the impact of the pandemic on employment status, consumer spending, food security, housing, education disruptions, and dimensions of physical and mental wellness (NCHS, 2024).
+Here the dataset is about the estimate of anxiety or depression under the mental wellness category.
+
+The estimand is the difference in whether a rate of symptoms of anxiety or depressive disorder of an individual would be correlated with the socio-cultural factors including age, sex, race/ethnicity, and education.
+
+This paper utilizes R (R Core Team 2020) for analysis, leveraging packages such as ggplot2(Wickham et al.
+2016) for creating graphical representations.
+Additionally, the gridExtra package was used to enhance the layout and presentation of the figures (Murrell 2021) !!+ add more packages that was used in the paper.
+!!
+
+The structure of the paper is ~
 
@@
 
-Weaknesses and next steps should also be included.
+The survey was designed to meet the goal of accurate and timely weekly estimates. Hence, it was conducted by an internet questionnaire, with invitations to participate sent by email and text message.
 

### 2024-04-02 scripts/02-data_cleaning.R

@@ -9,35 +9,13 @@
 #### Workspace setup ####
 library(tidyverse)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+# Rename the CSV files
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+#### Clean data ####
+raw_data <- read_csv("inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported.csv")
+
+# eliminate the rows subdivided By State, eliminate the columns Phase, Time Period, Time Period Label
+
 
 #### Save data ####
 write_csv(cleaned_data, "outputs/data/analysis_data.csv")

### 2024-04-02 outputs/paper/paper.qmd
update

@@
 date-format: long
-abstract: "Analyzing daata spanning from 2020 to 2024, we examine variatinos in anxiety or depressive disorders among different age groups, sex, race/ethnicity, and education level.
+abstract: "Analyzing data spanning from 2020 to 2024, we examine variatinos in anxiety or depressive disorders among different age groups, sex, race/ethnicity, and education level.
 Our analysis yncovers additional factors contributing to this trend.
@@
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-library(tidyverse)
-library(palmerpenguins)
-```
-
 # Introduction
-
-You can and should cross-reference sections and sub-sections.
-The remainder of this paper is structured as follows. @sec-data....
 
@@
 
-The structure of the paper is ~
+The structure of the paper is following, data is
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
-
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
 ### Model justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Results
-
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("outputs/models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
 

### 2024-04-02 outputs/paper/paper.qmd
Add introduction and abstract. Modify the references.bib file

@@
 date-format: long
-abstract: "Analyzing data spanning from 2020 to 2024, we examine variatinos in anxiety or depressive disorders among different age groups, sex, race/ethnicity, and education level.
-Our analysis yncovers additional factors contributing to this trend.
-"
+abstract: "This study explores how socio-cultural factors like age, sex, race/ethnicity, and education level influenced anxiety and depressive disorders in the U.S.
+during and after the COVID-19 pandemic, analyzing data from 2020 to 2024.
+Using advanced statistical methods in R, it uncovered significant variations in mental health impacts across different demographic groups.
+The research reveals a complex relationship between socio-cultural factors and mental health, highlighting the increased vulnerability of certain populations during global crises.
+These insights are crucial for developing targeted public health strategies to mitigate mental health issues during and after pandemics, enhancing our understanding of how socio-cultural dynamics shape mental wellness in times of crisis."
 format: pdf
@@
 
-Depression and anxiety are common symptoms of mental disorders in modern world.
-It could be light or serious.
-Someone could suffer it for longer period of time than the others, or someone could go through on a regular basis.
-It could be due to hormonal effect or circumstance that one confronting or even a weather can affect such level.
-!!According to ~ depression is ~ anxiety ~ !!
-It is not a country specific problem, but matters in the whole generation in global scale.
+Depression and anxiety are not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021).
+These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020).
+While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the nuanced interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).
 
-Due to the Covid-19 global pandemic, many countries took a lockdown measure and the US was not the exceptional.
-The U.S.
-Census Bureau launched the Household Pulse Survey to produce data on the social and economic impacts of Covid-19 on American households in collaboration with five federal agencies.
-The Household Pulse Survey was designed to gauge the impact of the pandemic on employment status, consumer spending, food security, housing, education disruptions, and dimensions of physical and mental wellness (NCHS, 2024).
-Here the dataset is about the estimate of anxiety or depression under the mental wellness category.
+This paper addresses this gap by analyzing data from the U.S.
+Census Bureau's Household Pulse Survey, initiated in response to the pandemic to assess its effects on American households, including mental wellness (U.S.
+Census Bureau, 2020).
+Our analysis focuses on the correlation between the prevalence of anxiety or depressive disorders and socio-cultural factors such as age, sex, race/ethnicity, and education level during the pandemic and post pandemic years of 2020 to 2024.
+Specifically, the estimand of this study is the difference in the rates of symptoms of anxiety or depressive disorders across individuals, correlated with socio-cultural factors including age, sex, race/ethnicity, and education level.
 
-The estimand is the difference in whether a rate of symptoms of anxiety or depressive disorder of an individual would be correlated with the socio-cultural factors including age, sex, race/ethnicity, and education.
+Employing a quantitative methodology, this paper utilizes R (R Core Team 2020) for analysis.
+We utilized packages like ggplot2 (Wickham et al., 2016) and gridExtra (Murrell, 2021) for data analysis and visualization.
+Our findings reveal significant trends and disparities in the rates of anxiety and depressive disorders across different socio-cultural groups, highlighting the intricate relationship between these factors and mental health outcomes during the pandemic.
 
-This paper utilizes R (R Core Team 2020) for analysis, leveraging packages such as ggplot2(Wickham et al.
-2016) for creating graphical representations.
-Additionally, the gridExtra package was used to enhance the layout and presentation of the figures (Murrell 2021) !!+ add more packages that was used in the paper.
-!!
+The importance of this research lies in its potential to inform public health policies and interventions, aiming to mitigate the adverse effects of such global crises on mental health (Xiong et al., 2020).
+By understanding the specific socio-cultural factors that contribute to increased vulnerability to anxiety and depressive disorders, targeted strategies can be developed to support affected populations more effectively.
 
-The structure of the paper is following, data is
+The paper is structured to first present the trend analysis of anxiety and depressive disorder rates in the U.S.
+from 2020 to 2024, followed by an examination of how these rates vary across different demographic groups.
+Subsequent sections delve into the statistical methods and results for each research question, culminating in a discussion that synthesizes the findings and explores their broader implications for mental health research and policy.
+The conclusion summarizes the key insights, acknowledges the limitations of the study, and suggests avenues for future research.
+
+The study focuses on answering the following research questions:
+
+* What is the trend in US anxiety and depressive disorder rates from 2020 to 2024?
+
+* How do anxiety and depressive rates vary across different age groups?
+
+* How do anxiety and depressive rates differ based on race and ethnicity?
+
+* How do anxiety and depressive rates differ based on sex?
+
+* How do anxiety and depressive rates differ based on education level?
 

### 2024-04-02 scripts/02-data_cleaning.R
commit

@@ -4,18 +4,5 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Pre-install package called janitor
-
-#### Workspace setup ####
-library(tidyverse)
-
-# Rename the CSV files
-
-#### Clean data ####
-raw_data <- read_csv("inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported.csv")
-
-# eliminate the rows subdivided By State, eliminate the columns Phase, Time Period, Time Period Label
-
-
-#### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+# Pre-requisites: Follow the 01-download_data.R steps, 
+# the paper uses the dataset from the original csv file without modification. 

### 2024-04-02 outputs/paper/paper.qmd
commit

@@
 
+## Methodology
+
+## Features
+
+# Results
+
+## Trend in US Anxiety and Depressive Disorder Rates
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-andtrend-graph
+#| fig-cap: "Trend in US Anxiety and Depressive Disorder Rates"
+
+install.packages("here")
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Load the dataset
+data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))
+
+# Filter the dataset for 'National Estimate' under 'Group' column and select indicators of interest
+
+filtered_data <- data %>%
+  filter(Group == "National Estimate" & Indicator %in% c("Symptoms of Anxiety Disorder", 
+                                                         "Symptoms of Depressive Disorder", 
+                                                         "Symptoms of Anxiety Disorder or Depressive Disorder"))
+
+# Create a YearMonth column from 'Time Period Label'
+
+filtered_data <- filtered_data %>%
+  mutate(YearMonth = as.Date(paste0(sub("^(\\d{4}).+", "\\1", `Time Period Label`), 
+                                    ".", 
+                                    sub(".+(\\d{2})$", "\\1", `Time Period Label`), 
+                                    "01"), format="%Y.%m.%d"))
+
+# Aggregate the data by YearMonth and Indicator
+aggregated_data <- filtered_data %>%
+  group_by(YearMonth, Indicator) %>%
+  summarise(AverageValue = mean(Value, na.rm = TRUE))
+
+# Plot the data
+ggplot(aggregated_data, aes(x = YearMonth, y = AverageValue, color = Indicator)) +
+  geom_line() +
+  scale_x_date(date_breaks = "6 months", date_labels = "%Y.%m") +
+  labs(
+    title = "National Estimates of Mental Health Symptoms",
+    subtitle = "Trends of Symptoms of Anxiety and Depressive Disorders",
+    x = "Year",
+    y = "Rate (%)",
+    color = "Indicator"
+  ) +
+  theme_minimal()
+
+```
+
+## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup
+
 # Model
@@
 
-# Results
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+## Findings
 
@@
 
-## Second discussion point
+## Ethical Implication
 
-## Third discussion point
-
-## Weaknesses and next steps
+## Limitation
 
 The survey was designed to meet the goal of accurate and timely weekly estimates. Hence, it was conducted by an internet questionnaire, with invitations to participate sent by email and text message.
+
+## Future Research
 
@@
 # References
+
+---
+nocite: '@*'
+---

### 2024-04-02 scripts/03-test_data.R

@@ -4,11 +4,52 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Pre-install necessary packages, tidyverse, lubridate, testthat
-
-
-#### Workspace setup ####
-library(tidyverse)
-
+# Pre-requisites: Pre-install necessary packages, readdr and testthat
 
 #### Test data ####
+# Load the necessary library
+library(testthat)
+library(readr)
+
+# Load the dataset from the CSV file
+data <- read.csv(file = here::here("downloads/Anxiety_depressive_disorder/inputs/data/Anxiety_or_Depression.csv"))
+
+# Convert Date to Date type and other necessary type conversions
+data$Date <- as.Date(data$Date, format="%Y-%m-%d")
+data$AgeGroup <- as.factor(data$AgeGroup)
+data$RaceEthnicity <- as.factor(data$RaceEthnicity)
+data$EducationLevel <- as.factor(data$EducationLevel)
+data$Sex <- as.factor(data$Sex)
+
+# Test the structure of the dataset
+test_that("Data structure is correct", {
+  expect_true(all(c("Date", "AgeGroup", "RaceEthnicity", "EducationLevel", "Sex", "AnxietyLevel", "DepressionLevel") %in% names(data)))
+  expect_type(data$Date, "Date")
+  expect_type(data$AgeGroup, "factor")
+  expect_type(data$AnxietyLevel, "numeric")
+  expect_type(data$DepressionLevel, "numeric")
+})
+
+# Test that anxiety and depression levels are within the expected range
+test_that("Anxiety and depression levels are within range", {
+  expect_true(all(data$AnxietyLevel >= 20 & data$AnxietyLevel <= 80))
+  expect_true(all(data$DepressionLevel >= 20 & data$DepressionLevel <= 80))
+})
+
+# Since the file does not contain aggregated data, this part might need adjustment
+# Assuming we create a summary (aggregated data) similar to the previous structure
+monthly_data <- data %>%
+  group_by(Date, AgeGroup) %>%
+  summarise(
+    AvgAnxiety = mean(AnxietyLevel, na.rm = TRUE),
+    AvgDepression = mean(DepressionLevel, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+# Test the aggregated data
+test_that("Aggregated data has correct structure and values", {
[…]

### 2024-04-02 scripts/03-test_data.R
update the WD

@@ -12,7 +12,7 @@ library(testthat)
 library(readr)
 
 # Load the dataset from the CSV file
-data <- read.csv(file = here::here("downloads/Anxiety_depressive_disorder/inputs/data/Anxiety_or_Depression.csv"))
+data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))
 
 # Convert Date to Date type and other necessary type conversions
 data$Date <- as.Date(data$Date, format="%Y-%m-%d")

### 2024-04-02 outputs/paper/paper.qmd
commit

@@
 
-install.packages("here")
+# Install the following package if wasn't installed already
+# install.packages("here")
 
@@
 # Load the dataset
-data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))
+data <- read.csv(file = here::here("inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"))
 
@@
 
-# Aggregate the data by YearMonth and Indicator
+# Check if the YearMonth column exists
+print(head(filtered_data))
+print(colnames(filtered_data))
+
+# Continue with the aggregation
 aggregated_data <- filtered_data %>%
-  group_by(YearMonth, Indicator) %>%
+  group_by(Time.Period.End.Date, Indicator) %>%
   summarise(AverageValue = mean(Value, na.rm = TRUE))
@@
 # Plot the data
-ggplot(aggregated_data, aes(x = YearMonth, y = AverageValue, color = Indicator)) +
+ggplot(aggregated_data, aes(x = Time.Period.End.Data, y = AverageValue, color = Indicator)) +
   geom_line() +

### 2024-04-02 scripts/02-data_cleaning.R

@@ -4,5 +4,4 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Follow the 01-download_data.R steps, 
-# the paper uses the dataset from the original csv file without modification. 
+# Pre-requisites: Follow the 01-download_data.R steps 

### 2024-04-02 outputs/paper/paper.qmd
Cleaned datasets and create csv files

--- 2024-04-02 outputs/paper/paper.qmd
@@
 
+## Methodology
+
+## Features
+
+# Results
+
+## Trend in US Anxiety and Depressive Disorder Rates
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-andtrend-graph
+#| fig-cap: "Trend in US Anxiety and Depressive Disorder Rates"
+
+```
+
+## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup
+
 # Model

### 2024-04-02 scripts/02-data_cleaning.R

@@ -4,4 +4,6 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Follow the 01-download_data.R steps 
+# Pre-requisites: Follow the 01-download_data.R steps
+
+

### 2024-04-02 scripts/02-data_cleaning.R
Data cleaning script updated

@@ -4,6 +4,63 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Follow the 01-download_data.R steps
+# Pre-requisites: Install package 'tidyverse'
 
+# Load the necessary library
+library(tidyverse)
+
+# Define the path to the raw data file
+raw_data_path <- "inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"
+
+# Load the raw data file
+raw_data <- read_csv(raw_data_path)
+
+#### Overall_trends #### 
+
+# Filter the dataset for 'National Estimate' group
+national_estimate_data <- raw_data %>%
+  filter(Group == "National Estimate" & 
+           Indicator %in% c("Symptoms of Anxiety Disorder or Depressive Disorder",
+                            "Symptoms of Depressive Disorder", 
+                            "Symptoms of Anxiety Disorder"))
+
+# Save the 'National Estimate' data to a new CSV file in the specified directory
+write_csv(national_estimate_data, "outputs/data/Overall_trends.csv")
+
+#### Subgroup trends - by age group cleaned dataset ####
+
+# Filter the dataset for 'By Age' group
+by_age_data <- raw_data %>%
+  filter(Group == "By Age")
+
+# Save the 'By Age' data to a new CSV file in the specified directory
+write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
+
+#### Subgroup trends - by sex group cleaned dataset ####
+
+# Filter the dataset for 'By Sex' group
+by_sex_data <- raw_data %>%
+  filter(Group == "By Sex")
+
+# Save the 'By Age' data to a new CSV file in the specified directory
+write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
+
+
+#### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
+
+# Filter the dataset for 'By Race/Hispanic ethnicity' group
+by_race_data <- raw_data %>%
+  filter(Group == "By Race/Hispanic ethnicity")
+
+# Save the 'By Age' data to a new CSV file in the specified directory
+write_csv(by_race_data, "outputs/data/Race_subgroup_trends.csv")
+
+#### Subgroup trends - by education group cleaned dataset ####
+
+# Filter the dataset for 'By Education' group
[…]

### 2024-04-03 scripts/01-download_data.R
Update the data cleaning script and subsequently subgroup data files

@@ -16,5 +16,5 @@
 # Step 6) Click Export button on the top right to export dataset. Before downloading the data, make sure it's set to download file and export format is in CSV.
 # Step 7) Search "Lack of Social Connection" 
 # Step 8) Click the dataset and check the data is provided by NCHS/DHIS and the publisher is National Center for Health Statistics
-# Step 8) Download the dataset by exporting it in CSV format
+# Step 9) Download the dataset by exporting it in CSV format
          

### 2024-04-03 scripts/02-data_cleaning.R

@@ -15,6 +15,9 @@ raw_data_path <- "inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Repor
 # Load the raw data file
 raw_data <- read_csv(raw_data_path)
 
+# Convert 'Time Period End Date' from string to date format in the raw_data dataframe
+raw_data$`Time Period End Date` <- as.Date(raw_data$`Time Period End Date`, format="%m/%d/%Y")
+
 #### Overall_trends #### 
 
 # Filter the dataset for 'National Estimate' group

### 2024-04-03 scripts/03-test_data.R

@@ -4,7 +4,7 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Pre-install necessary packages, readdr and testthat
+# Pre-requisites: Install necessary packages, readdr and testthat
 
 #### Test data ####
 # Load the necessary library
@@ -12,7 +12,7 @@ library(testthat)
 library(readr)
 
 # Load the dataset from the CSV file
-data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))
+data <- read.csv(file = here::here("inputs/data/Overall_trends.csv"))
 
 # Convert Date to Date type and other necessary type conversions
 data$Date <- as.Date(data$Date, format="%Y-%m-%d")

### 2024-04-03 outputs/paper/paper.qmd
commit

@@
 
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))
+
+# Convert 'Time Period End Date' to date format and then extract year and month
+data$`Time Period End Date` <- as.Date(data$`Time Period End Date`, format="%m/%d/%Y")
+data$YearMonth <- format(data$`Time Period End Date`, "%Y-%m")
+
+# Filter the dataset for the specified symptoms
+filtered_data <- data %>%
+  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
+                          'Symptoms of Anxiety Disorder', 
+                          'Symptoms of Anxiety Disorder or Depressive Disorder'))
+
+# Plotting the line graph
+ggplot(filtered_data, aes(x = YearMonth, y = Value, group = Indicator, color = Indicator)) +
+  geom_line() +
+  labs(title = "Symptom Rates Over Time",
+       x = "Date (Year and Month)",
+       y = "Symptom Rates (%)") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
 ```

### 2024-04-03 outputs/paper/paper.qmd
commit

--- 2024-04-02 outputs/paper/paper.qmd
@@
 
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))
+
+# Filter the dataset for the specified symptoms
+filtered_data <- data %>%
+  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
+                          'Symptoms of Anxiety Disorder', 
+                          'Symptoms of Anxiety Disorder or Depressive Disorder'))
+
+# Define the sequence of dates for x-axis breaks, starting from the first date, incrementing by 4 months
+start_date <- as.Date("2020-05-05")
+end_date <- as.Date("2024-03-04")
+
+# Manually define the specific dates you want to mark on the x-axis
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
+  geom_line() +
+  labs(title = "Overall Symptom Rates Trend",
+       x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
 ```

### 2024-04-03 scripts/02-data_cleaning.R
Cleaned data and save subgroups

@@ -18,10 +18,14 @@ raw_data <- read_csv(raw_data_path)
 # Convert 'Time Period End Date' from string to date format in the raw_data dataframe
 raw_data$`Time Period End Date` <- as.Date(raw_data$`Time Period End Date`, format="%m/%d/%Y")
 
+# Filter out rows where 'Value' column is empty
+nonempty_data <- raw_data %>%
+  filter(!is.na(Value) & Value != "")
+
 #### Overall_trends #### 
 
 # Filter the dataset for 'National Estimate' group
-national_estimate_data <- raw_data %>%
+national_estimate_data <- nonempty_data %>%
   filter(Group == "National Estimate" & 
            Indicator %in% c("Symptoms of Anxiety Disorder or Depressive Disorder",
                             "Symptoms of Depressive Disorder", 
@@ -33,7 +37,7 @@ write_csv(national_estimate_data, "outputs/data/Overall_trends.csv")
 #### Subgroup trends - by age group cleaned dataset ####
 
 # Filter the dataset for 'By Age' group
-by_age_data <- raw_data %>%
+by_age_data <- nonempty_data %>%
   filter(Group == "By Age")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -42,7 +46,7 @@ write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
 #### Subgroup trends - by sex group cleaned dataset ####
 
 # Filter the dataset for 'By Sex' group
-by_sex_data <- raw_data %>%
+by_sex_data <- nonempty_data %>%
   filter(Group == "By Sex")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -52,7 +56,7 @@ write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
 #### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
 
 # Filter the dataset for 'By Race/Hispanic ethnicity' group
-by_race_data <- raw_data %>%
+by_race_data <- nonempty_data %>%
   filter(Group == "By Race/Hispanic ethnicity")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -61,7 +65,7 @@ write_csv(by_race_data, "outputs/data/Race_subgroup_trends.csv")
 #### Subgroup trends - by education group cleaned dataset ####
 
 # Filter the dataset for 'By Education' group
-by_educ_data <- raw_data %>%
[…]

### 2024-04-03 outputs/paper/paper.qmd
commit

--- 2024-04-02 outputs/paper/paper.qmd
@@
 
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))
+
+# Filter the dataset for the specified symptoms
+filtered_data <- data %>%
+  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
+                          'Symptoms of Anxiety Disorder', 
+                          'Symptoms of Anxiety Disorder or Depressive Disorder'))
+
+# Ensure that 'Time.Period.End.Date' is a Date object
+filtered_data$Time.Period.End.Date <- as.Date(filtered_data$Time.Period.End.Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
+  geom_line() +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
+  labs(x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
 ```
 
+Both Anxiety and Depressive Disorder showing the similar trends over the period. 
 ## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-ageandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Age Subgroup in US"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))
+
+# Filter the dataset for the specified symptoms
+filtered_data <- data %>%
+  filter(Indicator == "Symptoms of Depressive Disorder")  # Assuming you need only this indicator
+
+# Ensure that 'Time Period End Date' is a Date object
+# Make sure to use the exact column name as it appears in your CSV file, including using backticks if necessary
+filtered_data$`Time Period End Date` <- as.Date(filtered_data$`Time Period End Date`, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(filtered_data, aes(x = `Time Period End Date`, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
+  labs(x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+```
 

### 2024-04-03 outputs/paper/paper.qmd
commite

@@
 # Plotting the line graph
-ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
+ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
   geom_line() +
@@
 Both Anxiety and Depressive Disorder showing the similar trends over the period.
+
 ## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup
@@
 filtered_data <- data %>%
-  filter(Indicator == "Symptoms of Depressive Disorder")  # Assuming you need only this indicator
-
-# Ensure that 'Time Period End Date' is a Date object
-# Make sure to use the exact column name as it appears in your CSV file, including using backticks if necessary
-filtered_data$`Time Period End Date` <- as.Date(filtered_data$`Time Period End Date`, format = "%Y-%m-%d")
+  filter(Indicator == "Symptoms of Depressive Disorder")
 
@@
 # Plotting the line graph
-ggplot(filtered_data, aes(x = `Time Period End Date`, y = Value, group = Subgroup, color = Subgroup)) +
+ggplot(filtered_data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
   geom_line() +

### 2024-04-03 scripts/02-data_cleaning.R

@@ -4,10 +4,11 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Install package 'tidyverse'
+# Pre-requisites: Install package 'tidyverse', 'dplyr'
 
 # Load the necessary library
 library(tidyverse)
+library(dplyr)
 
 # Define the path to the raw data file
 raw_data_path <- "inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"
@@ -22,10 +23,13 @@ raw_data$`Time Period End Date` <- as.Date(raw_data$`Time Period End Date`, form
 nonempty_data <- raw_data %>%
   filter(!is.na(Value) & Value != "")
 
+# Rename 'Time Period End Date' to 'Date'
+cleaned_data <- rename(nonempty_data, Date = `Time Period End Date`)
+
 #### Overall_trends #### 
 
 # Filter the dataset for 'National Estimate' group
-national_estimate_data <- nonempty_data %>%
+national_estimate_data <- cleaned_data %>%
   filter(Group == "National Estimate" & 
            Indicator %in% c("Symptoms of Anxiety Disorder or Depressive Disorder",
                             "Symptoms of Depressive Disorder", 
@@ -37,7 +41,7 @@ write_csv(national_estimate_data, "outputs/data/Overall_trends.csv")
 #### Subgroup trends - by age group cleaned dataset ####
 
 # Filter the dataset for 'By Age' group
-by_age_data <- nonempty_data %>%
+by_age_data <- cleaned_data %>%
   filter(Group == "By Age")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -46,7 +50,7 @@ write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
 #### Subgroup trends - by sex group cleaned dataset ####
 
 # Filter the dataset for 'By Sex' group
-by_sex_data <- nonempty_data %>%
+by_sex_data <- cleaned_data %>%
   filter(Group == "By Sex")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -56,7 +60,7 @@ write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
 #### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
 
[…]

### 2024-04-03 outputs/paper/paper.qmd
Only save depressive rows for the subgroups

@@
 # Ensure that 'Time.Period.End.Date' is a Date object
-filtered_data$Time.Period.End.Date <- as.Date(filtered_data$Time.Period.End.Date, format = "%Y-%m-%d")
+filtered_data$Date <- as.Date(filtered_data$Date, format = "%Y-%m-%d")
 
@@
 
+# Ensure that 'Time.Period.End.Date' is a Date object
+filtered_data$Date <- as.Date(filtered_data$Date, format = "%Y-%m-%d")
+
 # Define the specific dates for the x-axis scale
@@
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
-
 ```

### 2024-04-03 scripts/02-data_cleaning.R

@@ -40,8 +40,11 @@ write_csv(national_estimate_data, "outputs/data/Overall_trends.csv")
 
 #### Subgroup trends - by age group cleaned dataset ####
 
+# Filter the dataset to keep only rows where the 'Indicator' column is "Symptoms of Depressive Disorder"
+dep_data <- filter(cleaned_data, Indicator == "Symptoms of Depressive Disorder")
+
 # Filter the dataset for 'By Age' group
-by_age_data <- cleaned_data %>%
+by_age_data <- dep_data %>%
   filter(Group == "By Age")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -50,7 +53,7 @@ write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
 #### Subgroup trends - by sex group cleaned dataset ####
 
 # Filter the dataset for 'By Sex' group
-by_sex_data <- cleaned_data %>%
+by_sex_data <- dep_data %>%
   filter(Group == "By Sex")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -60,7 +63,7 @@ write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
 #### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
 
 # Filter the dataset for 'By Race/Hispanic ethnicity' group
-by_race_data <- cleaned_data %>%
+by_race_data <- dep_data %>%
   filter(Group == "By Race/Hispanic ethnicity")
 
 # Save the 'By Age' data to a new CSV file in the specified directory
@@ -69,7 +72,7 @@ write_csv(by_race_data, "outputs/data/Race_subgroup_trends.csv")
 #### Subgroup trends - by education group cleaned dataset ####
 
 # Filter the dataset for 'By Education' group
-by_educ_data <- cleaned_data %>%
+by_educ_data <- dep_data %>%
   filter(Group == "By Education")
 
 # Save the 'By Age' data to a new CSV file in the specified directory

### 2024-04-03 outputs/paper/paper.qmd
remove a word 'anxiety'

@@
 title: "Are we living in a depressive society?"
-subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"
+subtitle: "Trends in symptoms of depressive disorder in the US population from May 2020 to March 2024"
 author: Chay Park
@@
 date-format: long
-abstract: "This study explores how socio-cultural factors like age, sex, race/ethnicity, and education level influenced anxiety and depressive disorders in the U.S.
+abstract: "This study explores how socio-cultural factors like age, sex, race/ethnicity, and education level influenced depressive disorder in the U.S.
 during and after the COVID-19 pandemic, analyzing data from 2020 to 2024.
@@
 
-Depression and anxiety are not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021).
+Depression is not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021).
 These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020).
@@
 
-## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup
+## Trends in Depressive Disorder Rates by Population Subgroup
 
+### Population subgroup by age
 ```{r}
@@
 #| label: fig-ageandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Age Subgroup in US"
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age in US"
 
@@
 library(lubridate)
+library(here)
+library(ggplot2)
+library(gridExtra)
 
@@
 
-# Filter the dataset for the specified symptoms
-filtered_data <- data %>%
-  filter(Indicator == "Symptoms of Depressive Disorder")
-
-# Ensure that 'Time.Period.End.Date' is a Date object
-filtered_data$Date <- as.Date(filtered_data$Date, format = "%Y-%m-%d")
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
 
@@
 # Plotting the line graph
-ggplot(filtered_data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
+  labs(x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+```
+
+### Population subgroup by sex
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-sexandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex in US"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Sex_subgroup_trends.csv"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
+  labs(x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+```
+
+### Population subgroup by race
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-raceandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Race and Ethnicity in US"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
+  labs(x = "Date",
+       y = "Symptom Rates (%)") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "bottom",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+```
+
+### Population subgroup by education
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-sexandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex in US"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Sex_subgroup_trends.csv"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
   geom_line() +

### 2024-04-03 outputs/paper/paper.qmd
update

@@
 
-Depression is not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021).
+Depression and anxiety are not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021).
 These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020).
@@
        y = "Symptom Rates (%)") +
+  theme_classic() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
@@
 ### Population subgroup by age
+
 ```{r}
@@
 #| label: fig-ageandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age in US"
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup"
 
@@
 library(here)
-library(ggplot2)
-library(gridExtra)
+library(ggrepel)  # For better label placement
+library(dplyr)
 
@@
 
+# Define the specific date for placing the labels
+mid_date <- as.Date("2024-03-04")
+
+# Filter the data to get the rows for the specific date
+mid_date_data <- data %>%
+  filter(Date == mid_date)
+
 # Plotting the line graph
-ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
   geom_line() +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date",
-       y = "Symptom Rates (%)") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom",
+        legend.position = "none",  # Remove the separate legend
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Add labels to the lines with smaller font size
+p + geom_text_repel(
+  data = mid_date_data,
+  aes(label = Subgroup),
+  nudge_x = 0,  # Adjust this value based on your date range and aesthetics
+  nudge_y = 0,
+  direction = "y",
+  size = 3  # Adjust the size of the labels here; smaller values mean smaller text
+)
 
@@
 ### Population subgroup by sex
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-sexandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex in US"
-
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-library(here)
-
-# Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Sex_subgroup_trends.csv"))
-
-# Convert 'Date' column to Date format if it's not already
-data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
-
-# Define the specific dates for the x-axis scale
-specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
-                            "2021-05-10", "2021-09-13", "2022-01-10", 
-                            "2022-05-09", "2022-09-13", "2023-01-16",
-                            "2023-05-08", "2023-09-04", "2024-01-08"))
-
-# Plotting the line graph
-ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
-  geom_line() +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
-  labs(x = "Date",
-       y = "Symptom Rates (%)") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom",
-        plot.margin = unit(c(1, 1, 1, 1), "cm"))
-```
-
-### Population subgroup by race
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-raceandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Race and Ethnicity in US"
-
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-library(here)
-
-# Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))
-
-# Convert 'Date' column to Date format if it's not already
-data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
-
-# Define the specific dates for the x-axis scale
-specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
-                            "2021-05-10", "2021-09-13", "2022-01-10", 
-                            "2022-05-09", "2022-09-13", "2023-01-16",
-                            "2023-05-08", "2023-09-04", "2024-01-08"))
-
-# Plotting the line graph
-ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
-  geom_line() +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  
-  labs(x = "Date",
-       y = "Symptom Rates (%)") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom",
-        plot.margin = unit(c(1, 1, 1, 1), "cm"))
-```
-
-### Population subgroup by education
 ```{r}

### 2024-04-03 outputs/paper/paper.qmd
commit

@@
   geom_line() +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
@@
         legend.position = "bottom",
+        legend.box = "vertical",
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
@@
   geom_line() +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +

### 2024-04-03 outputs/paper/paper.qmd
Add subgroup figures

--- 2024-04-03 outputs/paper/paper.qmd
@@
                           'Symptoms of Anxiety Disorder', 
-                          'Symptoms of Anxiety Disorder or Depressive Disorder'))
+                          'Symptoms of Anxiety Disorder or Depressive Disorder')) %>%
+  mutate(Indicator = factor(Indicator, levels = c('Symptoms of Anxiety Disorder or Depressive Disorder',
+                                                  'Symptoms of Anxiety Disorder',
+                                                  'Symptoms of Depressive Disorder')))
 
@@
   geom_line() +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
+  geom_hline(yintercept = seq(10, 45, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
   labs(x = "Date",
@@
       legend.position = "bottom",
+      legend.box = "vertical",
+      legend.direction = "vertical",
       plot.margin = unit(c(1, 1, 1, 1), "cm"))
@@
 #| label: fig-ageandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup"
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"
 
@@
 library(here)
-library(ggrepel)  # For better label placement
-library(dplyr)
 
@@
 
-# Define the specific date for placing the labels
-mid_date <- as.Date("2024-03-04")
-
-# Filter the data to get the rows for the specific date
-mid_date_data <- data %>%
-  filter(Date == mid_date)
-
 # Plotting the line graph
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "none",  # Remove the separate legend
+        legend.position = "right",  # Position the legend on the right side of the plot
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
 
-# Add labels to the lines with smaller font size
-p + geom_text_repel(
-  data = mid_date_data,
-  aes(label = Subgroup),
-  nudge_x = 0,  # Adjust this value based on your date range and aesthetics
-  nudge_y = 0,
-  direction = "y",
-  size = 3  # Adjust the size of the labels here; smaller values mean smaller text
-)
+# Display the plot
+print(p)
 
@@
 ### Population subgroup by sex
+
 ```{r}
@@
 #| label: fig-sexandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex in US"
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Sex"
 
@@
 library(here)
+library(ggrepel)  # For better label placement
 
@@
 
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
 # Plotting the line graph
-ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
   geom_line() +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date",
-       y = "Symptom Rates (%)") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom",
+        legend.position = "none",  # Remove the separate legend
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+p + geom_text_repel(
+  data = label_data,
+  aes(label = Subgroup),
+  nudge_x = 0,  # Adjust nudge_x and nudge_y to correctly position the labels
+  nudge_y = 0,
+  direction = "y",
+  color = "black"
+)
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-raceandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Race"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_hline(yintercept = seq(5, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "right", 
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Display the plot
+print(p)
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-educandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Education"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+library(here)
+
+# Define the path to the data file and load it
+data <- read.csv(file = here::here("outputs/data/Educ_subgroup_trends.csv"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Plotting the line graph
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_hline(yintercept = seq(5, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "right", 
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Display the plot
+print(p)
 ```

### 2024-04-04 outputs/paper/paper.qmd
commit
figure

@@
 
-### Population subgroup by age
-
 ```{r}
@@
 #| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Read the data
+age_data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))
+
+# Ensure 'Date' column is in Date format
+age_data$Date <- as.Date(age_data$Date, format = "%Y-%m-%d")
+
+# Filter data to include only the relevant age subgroups
+filtered_data <- age_data %>%
+  filter(Subgroup %in% c("18 - 29 years", "30 - 39 years", "40 - 49 years", "50 - 59 years", "60 - 69 years", "70 - 79 years", "80 years and above"))
+
+# Specific date for labeling
+label_date <- as.Date("2022-03-02")
+
+# Prepare label data
+label_data <- filtered_data %>%
+  group_by(Subgroup) %>%
+  filter(Date == label_date) %>%
+  ungroup()
+
+# Plotting the line graph
+graph_A <- ggplot(filtered_data, aes(x = Date, y = Value, color = Subgroup)) +
+  geom_line(size = 0.4) +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
+  geom_text(data = label_data,
+            aes(label = Subgroup, y = Value + 2), hjust = 1.1, size = 3) +
+  scale_y_continuous(name = "Syptom Rates (%)") +
+  scale_x_date(date_breaks = "4 months", date_labels = "%Y-%m-%d") +
+  labs(title = "Trend of Depressive Disorder Symptoms by Age Group",
+       x = NULL,
+       y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = -45, hjust = 1),
+        plot.title = element_text(size = 10),
+        legend.position = "none")
+
+# Display the plot
+print(graph_A)
+
+```
+
+### Population subgroup by age
+
+```{r}
 

### 2024-04-04 outputs/paper/paper.qmd
commit

@@
 ```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-ageandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"
-
 # Load necessary libraries
@@
 library(lubridate)
+library(ggrepel)  # Ensure this package is installed for geom_text_repel
 
@@
 
-# Plotting the line graph
+# Plotting the line graph with labels
 graph_A <- ggplot(filtered_data, aes(x = Date, y = Value, color = Subgroup)) +
@@
   geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
-  geom_text(data = label_data,
-            aes(label = Subgroup, y = Value + 2), hjust = 1.1, size = 3) +
-  scale_y_continuous(name = "Syptom Rates (%)") +
+  geom_text_repel(
+    data = label_data,
+    aes(label = Subgroup),
+    nudge_y = 2,
+    direction = "y",
+    size = 3
+  ) +
+  scale_y_continuous(name = "Symptom Rates (%)") +
   scale_x_date(date_breaks = "4 months", date_labels = "%Y-%m-%d") +

### 2024-04-04 scripts/04-model.R
Update 04-model.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Chay Park
+# Date: 4 April 2024
+# Contact: chay.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-04-05 scripts/00-install_packages.R
commit

@@ -1,0 +1,25 @@
+#### Preamble ####
+# Purpose: Installs packages needed to run scripts and Quarto document
+# Author: Chay Park
+# Date: 4 April 2024
+# Contact: chay.park@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+## Installing packages (only needs to be done once per computer)
+install.packages("tidyverse") # Contains data-related packages
+install.packages("knitr") # To make tables
+install.packages("janitor") # To clean datasets
+install.packages("dplyr")
+install.packages("ggplot2") # To make graphs
+install.packages("usethis") 
+install.packages("arrow") # To allow Parquet files to be create
+install.packages("testthat") # To test
+
+# For models
+install.packages("beepr")
+install.packages("broom")
+install.packages("broom.mixed")
+install.packages("purrr")
+install.packages("rstanarm")
+install.packages("modelsummary")

### 2024-04-05 scripts/04-model.R
Update 04-model.R
working on model script

@@ -1,19 +1,23 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
+# Purpose: Models ....
 # Author: Chay Park
 # Date: 4 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
+
+#### Set seed for reproducibility ####
+set.seed(853)
 
 #### Read data ####
-analysis_data <- read_csv("outputs/data/analysis_data.csv")
+analysis_data <- read_parquet("outputs/data/analysis_data.csv")
+
+age_data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))
 
 ### Model data ####
 first_model <-

### 2024-04-05 scripts/02-data_cleaning.R
Update 02-data_cleaning.R
Save data file in parquet not CSV

@@ -35,8 +35,9 @@ national_estimate_data <- cleaned_data %>%
                             "Symptoms of Depressive Disorder", 
                             "Symptoms of Anxiety Disorder"))
 
-# Save the 'National Estimate' data to a new CSV file in the specified directory
-write_csv(national_estimate_data, "outputs/data/Overall_trends.csv")
+# Save the 'National Estimate' data to a new parquet file in the specified directory
+write_parquet(national_estimate_data, "outputs/data/Overall_trends.parquet")
+
 
 #### Subgroup trends - by age group cleaned dataset ####
 
@@ -47,8 +48,8 @@ dep_data <- filter(cleaned_data, Indicator == "Symptoms of Depressive Disorder")
 by_age_data <- dep_data %>%
   filter(Group == "By Age")
 
-# Save the 'By Age' data to a new CSV file in the specified directory
-write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_age_data, "outputs/data/Age_subgroup_trends.parquet")
 
 #### Subgroup trends - by sex group cleaned dataset ####
 
@@ -56,8 +57,8 @@ write_csv(by_age_data, "outputs/data/Age_subgroup_trends.csv")
 by_sex_data <- dep_data %>%
   filter(Group == "By Sex")
 
-# Save the 'By Age' data to a new CSV file in the specified directory
-write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_sex_data, "outputs/data/Sex_subgroup_trends.parquet")
 
 
 #### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
@@ -66,8 +67,8 @@ write_csv(by_sex_data, "outputs/data/Sex_subgroup_trends.csv")
 by_race_data <- dep_data %>%
   filter(Group == "By Race/Hispanic ethnicity")
 
-# Save the 'By Age' data to a new CSV file in the specified directory
-write_csv(by_race_data, "outputs/data/Race_subgroup_trends.csv")
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_race_data, "outputs/data/Race_subgroup_trends.parquet")
 
 #### Subgroup trends - by education group cleaned dataset ####
 
[…]

### 2024-04-05 scripts/02-data_cleaning.R
Save parquet files

@@ -9,6 +9,8 @@
 # Load the necessary library
 library(tidyverse)
 library(dplyr)
+library(janitor)
+library(arrow)
 
 # Define the path to the raw data file
 raw_data_path <- "inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"

### 2024-04-05 scripts/03-test_data.R
Updated test data, working on model script

@@ -1,18 +1,19 @@
 #### Preamble ####
 # Purpose: Tests the codes on the cleaned dataset 
 # Author: Chay Park
-# Date: 2 April 2024
+# Date: 4 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Install necessary packages, readdr and testthat
+# Pre-requisites: 00-install_packages, 01-download_data
 
 #### Test data ####
 # Load the necessary library
 library(testthat)
 library(readr)
+library(arrow)
 
-# Load the dataset from the CSV file
-data <- read.csv(file = here::here("inputs/data/Overall_trends.csv"))
+# Load the dataset from the parquet file
+data <- read_parquet(file = here::here("inputs/data/Overall_trends.parquet"))
 
 # Convert Date to Date type and other necessary type conversions
 data$Date <- as.Date(data$Date, format="%Y-%m-%d")

### 2024-04-05 scripts/04-model.R

@@ -4,7 +4,7 @@
 # Date: 4 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
+# Pre-requisites: 00-install_packages
 
 #### Workspace setup ####
 library(tidyverse)
@@ -15,15 +15,13 @@ library(arrow)
 set.seed(853)
 
 #### Read data ####
-analysis_data <- read_parquet("outputs/data/analysis_data.csv")
-
-age_data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))
+age_data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
 
 ### Model data ####
-first_model <-
+age_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
+    formula = Value_time ~ length + width,
+    data = age_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -34,8 +32,8 @@ first_model <-
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "outputs/models/first_model.rds"
+  age_model,
+  file = "outputs/models/age_model.rds"
 )
 
 

### 2024-04-05 scripts/04-model.R
Update 04-model.R

@@ -17,10 +17,15 @@ set.seed(853)
 #### Read data ####
 age_data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
 
+# Convert categorical variables to factors
+age_data$Subgroup <- as.factor(age_data$Subgroup)
+age_data$`Time Period` <- as.factor(age_data$`Time Period`)
+
 ### Model data ####
+# Assuming 'Value' is the dependent variable, and you want to model it based on 'Time Period' and 'Subgroup'
 age_model <-
   stan_glm(
-    formula = Value_time ~ length + width,
+    formula = Value ~ `Time Period` + Subgroup,
     data = age_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -28,7 +33,6 @@ age_model <-
     prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
-
 
 #### Save model ####
 saveRDS(

### 2024-04-05 scripts/04-model.R
Add purpose on preamble for model script

@@ -1,5 +1,6 @@
 #### Preamble ####
-# Purpose: Models ....
+# Purpose: Models relationship between the Value and various demographic and temporal factors 
+#          in the Age_subgroup_trends dataset to understand trends over time and across different subgroups.
 # Author: Chay Park
 # Date: 4 April 2024
 # Contact: chay.park@mail.utoronto.ca

### 2024-04-05 outputs/paper/paper.qmd
commit

--- 2024-04-03 outputs/paper/paper.qmd
@@
 ---
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# Load necessary libraries for the paper
+library(tidyverse)
+library(lubridate)
+library(arrow)
+library(here)
+library(ggrepel)  # For better label placement
+
+```
 
@@
 
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-
 # Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))
+data <- read_parquet(file = here::here("outputs/data/Overall_trends.parquet"))
 
@@
 
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-library(here)
-
 # Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))
+data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
 
@@
 
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-library(here)
-library(ggrepel)  # For better label placement
-
 # Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Sex_subgroup_trends.csv"))
+data <- read_parquet(file = here::here("outputs/data/Sex_subgroup_trends.parquet"))
 
@@
 # Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))
+data <- read_parquet(file = here::here("outputs/data/Race_subgroup_trends.parquet"))
 
@@
 
-# Load necessary libraries
-library(tidyverse)
-library(lubridate)
-library(here)
-
 # Define the path to the data file and load it
-data <- read.csv(file = here::here("outputs/data/Educ_subgroup_trends.csv"))
+data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
 
@@
 # Discussion
+
+What is done in this paper? 
+What is something that we learn about the world? 
+What is another thing that we learn about the world? 
+What are some weaknesses of what was done? 
+What is left to learn or how should we proceed in the future?
 

### 2024-04-05 scripts/01-download_data.R
Update 01-download_data.R
Add a line of explanation

@@ -14,7 +14,8 @@
 # Step 4) Click a data set with a title "Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days"
 # Step 5) Double check the data is provided by NCHS/DHIS and the publisher is National Center for Health Statistics
 # Step 6) Click Export button on the top right to export dataset. Before downloading the data, make sure it's set to download file and export format is in CSV.
+
+# Follow the similar procedure for other dataset
 # Step 7) Search "Lack of Social Connection" 
 # Step 8) Click the dataset and check the data is provided by NCHS/DHIS and the publisher is National Center for Health Statistics
 # Step 9) Download the dataset by exporting it in CSV format
-         

### 2024-04-05 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -4,7 +4,7 @@
 # Date: 2 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Install package 'tidyverse', 'dplyr'
+# Pre-requisites: 00-install_packages, 01-download_data
 
 # Load the necessary library
 library(tidyverse)

### 2024-04-05 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -1,7 +1,7 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by National Center for Health Statistics
+# Purpose: Cleans the raw plane datas recorded by National Center for Health Statistics
 # Author: Chay Park
-# Date: 2 April 2024
+# Date: 4 April 2024
 # Contact: chay.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 00-install_packages, 01-download_data

### 2024-04-05 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -6,11 +6,15 @@
 # License: MIT
 # Pre-requisites: 00-install_packages, 01-download_data
 
+#### Workplace setup ####
+
 # Load the necessary library
 library(tidyverse)
 library(dplyr)
 library(janitor)
 library(arrow)
+
+#### Main dataset cleaning ####
 
 # Define the path to the raw data file
 raw_data_path <- "inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"
@@ -39,6 +43,79 @@ national_estimate_data <- cleaned_data %>%
 
 # Save the 'National Estimate' data to a new parquet file in the specified directory
 write_parquet(national_estimate_data, "outputs/data/Overall_trends.parquet")
+
+
+#### Subgroup trends - by age group cleaned dataset ####
+
+# Filter the dataset to keep only rows where the 'Indicator' column is "Symptoms of Depressive Disorder"
+dep_data <- filter(cleaned_data, Indicator == "Symptoms of Depressive Disorder")
+
+# Filter the dataset for 'By Age' group
+by_age_data <- dep_data %>%
+  filter(Group == "By Age")
+
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_age_data, "outputs/data/Age_subgroup_trends.parquet")
+
+#### Subgroup trends - by sex group cleaned dataset ####
+
+# Filter the dataset for 'By Sex' group
+by_sex_data <- dep_data %>%
+  filter(Group == "By Sex")
+
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_sex_data, "outputs/data/Sex_subgroup_trends.parquet")
+
+
+#### Subgroup trends - by race/hispanic ethnicity group cleaned dataset ####
+
+# Filter the dataset for 'By Race/Hispanic ethnicity' group
+by_race_data <- dep_data %>%
+  filter(Group == "By Race/Hispanic ethnicity")
+
+# Save the 'By Age' data to a new parquet file in the specified directory
+write_parquet(by_race_data, "outputs/data/Race_subgroup_trends.parquet")
+
+#### Subgroup trends - by education group cleaned dataset ####
+
+# Filter the dataset for 'By Education' group
+by_educ_data <- dep_data %>%
+  filter(Group == "By Education")
+
+# Save the 'By Age' data to a new parquet file in the specified directory
[…]

### 2024-04-05 outputs/paper/paper.qmd
install new package

@@
   geom_line() +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
@@
   geom_line() +
-  geom_hline(yintercept = seq(5, 40, by = 5), color = "lightgrey") +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "right", 
+        legend.position = "bottom", 
+        legend.box = "vertical",
+        legend.direction = "vertical",
         plot.margin = unit(c(1, 1, 1, 1), "cm"))

### 2024-04-05 scripts/00-install_packages.R

@@ -15,6 +15,7 @@ install.packages("ggplot2") # To make graphs
 install.packages("usethis") 
 install.packages("arrow") # To allow Parquet files to be create
 install.packages("testthat") # To test
+install.packages("patchwork")
 
 # For models
 install.packages("beepr")

### 2024-04-05 outputs/paper/paper.qmd
commite

@@
 
+library(tidyverse)
+library(arrow)
+library(here)
+library(ggrepel)
+library(extrafont)
+
+# Load the fonts
+loadfonts(device = "win")
+
 # Define the path to the data file and load it
@@
 data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Bachelor's degree or higher" = "College graduate",
+                        "High school diploma or GED" = "High school graduate",
+                        "Some college/Associate's degree" = "Some college",
+                        "Less than a high school diploma" = "No high school degree")
 
@@
 
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  filter(Date == max(Date)) %>%
+  ungroup()
+
 # Plotting the line graph
@@
   geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), nudge_x = 10, nudge_y = 0, family = "Times New Roman") +
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom", 
-        legend.box = "vertical",
-        legend.direction = "vertical",
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
 
-# Display the plot
 print(p)
+
 ```

### 2024-04-05 scripts/00-install_packages.R

@@ -16,6 +16,7 @@ install.packages("usethis")
 install.packages("arrow") # To allow Parquet files to be create
 install.packages("testthat") # To test
 install.packages("patchwork")
+install.packages("extrafont")
 
 # For models
 install.packages("beepr")

### 2024-04-05 outputs/paper/paper.qmd
commit

--- 2024-04-05 outputs/paper/paper.qmd
@@
 library(tidyverse)
-library(lubridate)
+library(arrow)
 library(here)
+library(ggrepel)
+library(extrafont)
+
+# Load the fonts
+loadfonts(device = "win")
 
@@
 
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Hispanic or Latino" = "Hispanic",
+                        "Non-Hispanic Asian, single race" = "Asian",
+                        "Non-Hispanic Black, single race" = "African American",
+                        "Non-Hispanic White, single race" = "Caucasian",
+                        "Non-Hispanic, other races and multiple races" = "Other")
+
 # Define the specific dates for the x-axis scale
@@
 
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  summarize(Date = median(Date), Value = median(Value)) %>%
+  ungroup()
+
 # Plotting the line graph
@@
   geom_line() +
-  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  geom_label_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                   nudge_x = 10, nudge_y = 0, family = "Times New Roman", color = "black",
+                   box.padding = 0.35, point.padding = 0.5, 
+                   arrow = arrow(length = unit(0.02, "npc")),
+                   size = 3) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey", lty = 2) +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "bottom", 
-        legend.box = "vertical",
-        legend.direction = "vertical",
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
@@
 
-# Plotting the line graph
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  summarize(Date = median(Date), Value = median(Value)) %>%
+  ungroup()
+
+# Plotting the line graph with adjusted label positions
 p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
   geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  nudge_y = 2, family = "Times New Roman", 
+                  direction = "y", box.padding = 0.5) +  # Adjust these parameters as needed
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +

### 2024-04-05 outputs/paper/paper.qmd
commit

@@
 ```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-ageandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"
+
+# Load necessary libraries
+library(tidyverse)
+library(arrow)
+library(here)
+library(ggrepel)
+library(extrafont)
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times New Roman", color = "black",
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Display the plot
+print(p)
+
+```
 
@@
 
-# Prepare data for labels
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
 label_data <- data %>%
-  group_by(Subgroup) %>%
-  summarize(Date = median(Date), Value = median(Value)) %>%
-  ungroup()
+  filter(Date == label_date)
 
@@
   geom_line() +
-  geom_label_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                   nudge_x = 10, nudge_y = 0, family = "Times New Roman", color = "black",
-                   box.padding = 0.35, point.padding = 0.5, 
-                   arrow = arrow(length = unit(0.02, "npc")),
-                   size = 3) +
-  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey", lty = 2) +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  nudge_x = 0, nudge_y = 0, family = "Times New Roman", color = "black",
+                  size = 3,  # Make label text smaller
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), ends = "last", angle = 30)) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
   scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
@@
 
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph with adjusted label positions
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  nudge_y = 2, family = "Times New Roman", 
+                  direction = "y", box.padding = 0.5) +  # Adjust these parameters as needed
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+print(p)
+
+```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-educandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Education"
+
+library(tidyverse)
+library(arrow)
+library(here)
+library(ggrepel)
+library(extrafont)
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Bachelor's degree or higher" = "College graduate",
+                        "High school diploma or GED" = "High school graduate",
+                        "Some college/Associate's degree" = "Some college",
+                        "Less than a high school diploma" = "No high school degree")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
 # Prepare data for labels
@@
   geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  nudge_y = 2, family = "Times New Roman", 
-                  direction = "y", box.padding = 0.5) +  # Adjust these parameters as needed
+                  family = "Times New Roman", color = "black",
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 30),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+print(p)
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-educandtrend-graph
+#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Education"
+
+library(tidyverse)
+library(arrow)
+library(here)
+library(ggrepel)
+library(extrafont)
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Bachelor's degree or higher" = "College graduate",
+                        "High school diploma or GED" = "High school graduate",
+                        "Some college/Associate's degree" = "Some college",
+                        "Less than a high school diploma" = "No high school degree")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  summarize(Date = median(Date), Value = median(Value)) %>%
+  ungroup()
+
+# Plotting the line graph with adjusted label positions
+p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times New Roman", 
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 30),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +

### 2024-04-05 outputs/paper/paper.qmd
Upgraded the plot figure

@@
 library(ggrepel)  # For better label placement
+library(extrafont)
 
@@
 
+# Load the fonts
+loadfonts(device = "win")
+
 # Define the path to the data file and load it
@@
 # Plotting the line graph
-ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
+p <- ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
   geom_line() +
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
         legend.position = "bottom",
@@
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Display the plot
+print(p)
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-ageandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Age"
-
-# Define the path to the data file and load it
-data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
-
-# Convert 'Date' column to Date format if it's not already
-data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
-
-# Define the specific dates for the x-axis scale
-specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
-                            "2021-05-10", "2021-09-13", "2022-01-10", 
-                            "2022-05-09", "2022-09-13", "2023-01-16",
-                            "2023-05-08", "2023-09-04", "2024-01-08"))
-
-# Plotting the line graph
-p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
-  geom_line() +
-  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "right",  # Position the legend on the right side of the plot
-        plot.margin = unit(c(1, 1, 1, 1), "cm"))
-
-# Display the plot
-print(p)
-
-```
 ```{r}
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
         legend.position = "none",  # Remove the separate legend
@@
   direction = "y",
-  color = "black"
+  color = "black",
+  family = "Times New Roman"
 )
@@
 
-# Filter the data to get the rows for the specific date to label
-label_date <- as.Date("2022-01-10")
-label_data <- data %>%
-  filter(Date == label_date)
-
-# Plotting the line graph with adjusted label positions
-p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
-  geom_line() +
-  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  nudge_y = 2, family = "Times New Roman", 
-                  direction = "y", box.padding = 0.5) +  # Adjust these parameters as needed
-  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
-        legend.position = "none",
-        plot.margin = unit(c(1, 1, 1, 1), "cm"))
-
-print(p)
-
-```
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-educandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Education"
-
-library(tidyverse)
-library(arrow)
-library(here)
-library(ggrepel)
-library(extrafont)
-
-# Load the fonts
-loadfonts(device = "win")
-
-# Define the path to the data file and load it
-data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
-
-# Convert 'Date' column to Date format if it's not already
-data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
-
-# Rename the subgroup values
-data$Subgroup <- recode(data$Subgroup,
-                        "Bachelor's degree or higher" = "College graduate",
-                        "High school diploma or GED" = "High school graduate",
-                        "Some college/Associate's degree" = "Some college",
-                        "Less than a high school diploma" = "No high school degree")
-
-# Define the specific dates for the x-axis scale
-specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
-                            "2021-05-10", "2021-09-13", "2022-01-10", 
-                            "2022-05-09", "2022-09-13", "2023-01-16",
-                            "2023-05-08", "2023-09-04", "2024-01-08"))
-
-# Prepare data for labels
-label_data <- data %>%
-  group_by(Subgroup) %>%
-  summarize(Date = median(Date), Value = median(Value)) %>%
-  ungroup()
-
-# Plotting the line graph with adjusted label positions
-p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
-  geom_line() +
-  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  family = "Times New Roman", color = "black",
-                  size = 3,  # Smaller text size
-                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 30),
-                  box.padding = unit(0.5, "lines"),
-                  point.padding = unit(0.5, "lines")) +
-  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
-        legend.position = "none",
-        plot.margin = unit(c(1, 1, 1, 1), "cm"))
-
-print(p)
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-educandtrend-graph
-#| fig-cap: "Depressive Disorder Trend by Population Subgroup by Education"
-
-library(tidyverse)
-library(arrow)
-library(here)
-library(ggrepel)
-library(extrafont)
-
-# Load the fonts
-loadfonts(device = "win")
-
-# Define the path to the data file and load it
-data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
-
-# Convert 'Date' column to Date format if it's not already
-data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
-
-# Rename the subgroup values
-data$Subgroup <- recode(data$Subgroup,
-                        "Bachelor's degree or higher" = "College graduate",
-                        "High school diploma or GED" = "High school graduate",
-                        "Some college/Associate's degree" = "Some college",
-                        "Less than a high school diploma" = "No high school degree")
-
-# Define the specific dates for the x-axis scale
-specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
-                            "2021-05-10", "2021-09-13", "2022-01-10", 
-                            "2022-05-09", "2022-09-13", "2023-01-16",
-                            "2023-05-08", "2023-09-04", "2024-01-08"))
-
 # Prepare data for labels
@@
 print(p)
+
+```
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-subtrend-graph
+#| fig-cap: "Depressive Disorder Trends by Population Subgroup"
+
+# Set seed for reproducibility
+set.seed()
+
+#### Graph A ####
 

### 2024-04-05 outputs/paper/paper.qmd
je suis fatiguee

@@
 library(extrafont)
+library(ggplot2)
+library(gridExtra)
 
@@
 # Set seed for reproducibility
-set.seed()
+set.seed(24)
 
-#### Graph A ####
+#### Graph A - Age ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_a <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times New Roman", color = "black",
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+#### Graph B - Sex ####
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Sex_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_b <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = "Date", y = "Symptom Rates (%)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_text(family = "Times New Roman"),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",  # Remove the separate legend
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+graph_b + geom_text_repel(
+  data = label_data,
+  aes(label = Subgroup),
+  nudge_x = 0,  # Adjust nudge_x and nudge_y to correctly position the labels
+  nudge_y = 0,
+  direction = "y",
+  color = "black",
+  family = "Times New Roman"
+)
+
+#### Graph C - Race ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Race_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Hispanic or Latino" = "Hispanic",
+                        "Non-Hispanic Asian, single race" = "Asian",
+                        "Non-Hispanic Black, single race" = "African American",
+                        "Non-Hispanic White, single race" = "Caucasian",
+                        "Non-Hispanic, other races and multiple races" = "Other")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_c <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  nudge_x = 0, nudge_y = 0, family = "Times New Roman", color = "black",
+                  size = 3,  # Make label text smaller
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), ends = "last", angle = 15)) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = "Symptom Rates (%)", title = "C: Race Subgroups Trends") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_text(family = "Times New Roman"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+#### Graph D - Education ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Bachelor's degree or higher" = "College graduate",
+                        "High school diploma or GED" = "High school graduate",
+                        "Some college/Associate's degree" = "Some college",
+                        "Less than a high school diploma" = "No high school degree")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  summarize(Date = median(Date), Value = median(Value)) %>%
+  ungroup()
+
+# Plotting the line graph with adjusted label positions
+graph_d <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times New Roman", 
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = NULL, title = "D: Level of education") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
+        axis.text.y = element_text(family = "Times New Roman"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Arrange graphs 2 x 2 grid
+grid.arrange(graph_a, graph_b, graph_c, graph_d, ncol = 2, nrow = 2)
 

### 2024-04-05 outputs/paper/paper.qmd
commit

--- 2024-04-05 outputs/paper/paper.qmd
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "bottom",
@@
   geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  family = "Times New Roman", color = "black",
+                  family = "Times", color = "black",
                   size = 3,  # Smaller text size
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",
@@
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",  # Remove the separate legend
@@
   color = "black",
-  family = "Times New Roman"
+  family = "Times"
 )
@@
   geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  nudge_x = 0, nudge_y = 0, family = "Times New Roman", color = "black",
+                  nudge_x = 0, nudge_y = 0, family = "Times", color = "black",
                   size = 3,  # Make label text smaller
@@
   geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  family = "Times New Roman", 
+                  family = "Times", 
                   size = 3,  # Smaller text size
@@
 # Set seed for reproducibility
-set.seed()
+set.seed(24)
 
-#### Graph A ####
+#### Graph A - Age ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_a <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times", color = "black",
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = "Symptom Rates (%)", title = "A: Age Subgroup Trends") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_text(family = "Times"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+#### Graph B - Sex ####
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Sex_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_b <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = "Symptom Rates (%)",title = "C: Sex Subgroup Trends") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_text(family = "Times"),
+        legend.position = "none", 
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+graph_b + geom_text_repel(
+  data = label_data,
+  aes(label = Subgroup),
+  nudge_x = 0,  # Adjust nudge_x and nudge_y to correctly position the labels
+  nudge_y = 0,
+  direction = "y",
+  color = "black",
+  family = "Times"
+)
+
+#### Graph C - Race ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Race_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Hispanic or Latino" = "Hispanic",
+                        "Non-Hispanic Asian, single race" = "Asian",
+                        "Non-Hispanic Black, single race" = "African American",
+                        "Non-Hispanic White, single race" = "Caucasian",
+                        "Non-Hispanic, other races and multiple races" = "Other")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Filter the data to get the rows for the specific date to label
+label_date <- as.Date("2022-01-10")
+label_data <- data %>%
+  filter(Date == label_date)
+
+# Plotting the line graph
+graph_c <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  nudge_x = 0, nudge_y = 0, family = "Times", color = "black",
+                  size = 3,  # Make label text smaller
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), ends = "last", angle = 15)) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = "Symptom Rates (%)", title = "C: Race Subgroups Trends") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_text(family = "Times"),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+#### Graph D - Education ####
+
+# Load the fonts
+loadfonts(device = "win")
+
+# Define the path to the data file and load it
+data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))
+
+# Convert 'Date' column to Date format if it's not already
+data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
+
+# Rename the subgroup values
+data$Subgroup <- recode(data$Subgroup,
+                        "Bachelor's degree or higher" = "College graduate",
+                        "High school diploma or GED" = "High school graduate",
+                        "Some college/Associate's degree" = "Some college",
+                        "Less than a high school diploma" = "No high school degree")
+
+# Define the specific dates for the x-axis scale
+specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
+                            "2021-05-10", "2021-09-13", "2022-01-10", 
+                            "2022-05-09", "2022-09-13", "2023-01-16",
+                            "2023-05-08", "2023-09-04", "2024-01-08"))
+
+# Prepare data for labels
+label_data <- data %>%
+  group_by(Subgroup) %>%
+  summarize(Date = median(Date), Value = median(Value)) %>%
+  ungroup()
+
+# Plotting the line graph with adjusted label positions
+graph_d <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
+  geom_line() +
+  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
+                  family = "Times", 
+                  size = 3,  # Smaller text size
+                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
+                  box.padding = unit(0.5, "lines"),
+                  point.padding = unit(0.5, "lines")) +
+  geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  labs(x = NULL, y = NULL, title = "D: Level of education") +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        legend.position = "none",
+        plot.margin = unit(c(1, 1, 1, 1), "cm"))
+
+# Arrange graphs 2 x 2 grid
+grid.arrange(graph_a, graph_b, graph_c, graph_d, ncol = 2, nrow = 2)
 

### 2024-04-08 outputs/paper/paper.qmd
commit

--- 2024-04-05 outputs/paper/paper.qmd
@@
 
-* How do anxiety and depressive rates vary across different age groups?
+* How do depressive rates vary across different age groups?
 
-* How do anxiety and depressive rates differ based on race and ethnicity?
+* How do depressive rates differ based on race and ethnicity?
 
-* How do anxiety and depressive rates differ based on sex?
+* How do depressive rates differ based on sex?
 
-* How do anxiety and depressive rates differ based on education level?
+* How do adepressive rates differ based on education level?
+
+* Is there codependency of social connection on one's depression level?
 
@@
   geom_hline(yintercept = seq(10, 45, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date",
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m") +
+  labs(x = NULL,
        y = "Symptom Rates (%)") +
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "bottom",
@@
   geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m") +
+  labs(x = NULL, y = "Symptom Rates (%)") +
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",
@@
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m") +
+  labs(x = NULL, y = "Symptom Rates (%)") +
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",  # Remove the separate legend
@@
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
-  labs(x = "Date", y = "Symptom Rates (%)") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m") +
+  labs(x = NULL, y = "Symptom Rates (%)") +
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",
@@
   geom_hline(yintercept = seq(0, 40, by = 5), color = "lightgrey") +
-  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
+  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m") +
   labs(x = "Date", y = "Symptom Rates (%)") +
   theme_classic() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times New Roman"),
-        axis.text.y = element_text(family = "Times New Roman"),
-        axis.title.x = element_text(family = "Times New Roman"),
-        axis.title.y = element_text(family = "Times New Roman"),
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Times"),
+        axis.text.y = element_text(family = "Times"),
+        axis.title.x = element_text(family = "Times"),
+        axis.title.y = element_text(family = "Times"),
         legend.position = "none",
@@
 print(p)
-
-```
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-subtrend-graph
-#| fig-cap: "Depressive Disorder Trends by Population Subgroup"
-
-# Set seed for reproducibility
-set.seed()
-
-#### Graph A ####
 

### 2024-04-08 scripts/02-data_cleaning.R

@@ -157,3 +157,4 @@ by_educ_data <- dep_data %>%
 
 # Save the 'By Age' data to a new parquet file in the specified directory
 write_parquet(by_educ_data, "outputs/data/Educ_subgroup_trends.parquet")
+

### 2024-04-08 scripts/02-data_cleaning.R
second data file processing

@@ -158,3 +158,23 @@ by_educ_data <- dep_data %>%
 # Save the 'By Age' data to a new parquet file in the specified directory
 write_parquet(by_educ_data, "outputs/data/Educ_subgroup_trends.parquet")
 
+
+#### Second data ####
+
+# Path to your raw CSV file
+social_csv_file_path <- "inputs/data/Lack_of_Social_Connection.csv"
+
+# Read the CSV file into a dataframe
+data <- read.csv(social_csv_file_path)
+
+# Specify the path for the output Parquet file
+parquet_file_path <- "outputs/data/Social_Connection.parquet"
+
+# Write the dataframe to a Parquet file
+write_parquet(data, parquet_file_path)
+
+# Save it in CSV format to view the files
+
+# Specify the path for the output CSV file
+csv_file_path <- "outputs/data/Social_Connection.csv"
+write_csv(data, csv_file_path)

### 2024-04-08 outputs/paper/paper.qmd
lack of social data analysis

@@
 ```
+```{r}
+
+# Define the path to the data file and load it
+social_data <- read_parquet(file = here::here("outputs/data/Social_Connection.parquet"))
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Age" subgroup
+filtered_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Age")
+
+# Plot the stacked bar chart
+ggplot(filtered_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Age",
+       x = "Time Period",
+       y = "Value") +
+  theme_minimal()
+
+```
 

### 2024-04-08 outputs/paper/paper.qmd
commit social data

--- 2024-04-08 outputs/paper/paper.qmd
@@
 ```
+```{r}
+
+# Define the path to the data file and load it
+social_data <- read_parquet(file = here::here("outputs/data/Social_Connection.parquet"))
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Age" subgroup
+social_age_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Age")
+
+# Plot the stacked bar chart
+ggplot(social_age_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Age",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Sex" subgroup
+social_sex_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Sex")
+
+# Plot the stacked bar chart
+ggplot(social_sex_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Sex",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Race/Hispanic ethnicity" subgroup
+social_race_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Race/Hispanic ethnicity")
+
+# Plot the stacked bar chart
+ggplot(social_race_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Race",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Education" subgroup
+social_educ_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Education")
+
+# Plot the stacked bar chart
+ggplot(social_educ_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Education",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+```
 

### 2024-04-08 outputs/paper/paper.qmd
pane

--- 2024-04-08 outputs/paper/paper.qmd
@@
 ```
+```{r}
+
+# Define the path to the data file and load it
+social_data <- read_parquet(file = here::here("outputs/data/Social_Connection.parquet"))
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Age" subgroup
+social_age_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Age")
+
+# Plot the stacked bar chart
+graph_age <- ggplot(social_age_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Age",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Sex" subgroup
+social_sex_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Sex")
+
+# Plot the stacked bar chart
+graph_sex <- ggplot(social_sex_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Sex",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Race/Hispanic ethnicity" subgroup
+social_race_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Race/Hispanic ethnicity")
+
+# Plot the stacked bar chart
+graph_race <- ggplot(social_race_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Race",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Filter data for the indicator "Adults who usually or always feel lonely" and "By Education" subgroup
+social_educ_data <- social_data %>%
+  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Education")
+
+# Plot the stacked bar chart
+graph_educ <- ggplot(social_educ_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Adults who usually or always feel lonely - By Education",
+       x = NULL,
+       y = "Value") +
+  theme_minimal()
+
+# Arrange graphs in single pane
+grid.arrange(graph_age, graph_sex, graph_race, graph_educ, nrow = 2, ncol = 2)
+
+```
 

### 2024-04-08 outputs/paper/paper.qmd
Update paper.qmd
Edit Intro and abstract

@@
 The research reveals a complex relationship between socio-cultural factors and mental health, highlighting the increased vulnerability of certain populations during global crises.
-These insights are crucial for developing targeted public health strategies to mitigate mental health issues during and after pandemics, enhancing our understanding of how socio-cultural dynamics shape mental wellness in times of crisis."
+The findings contribute to the development of targeted public health measures to alleviate mental health issues amid and following pandemics, enhancing our understanding of the impact of socio-cultural factors on mental well-being in times of crisis."
 format: pdf

### 2024-04-11 outputs/paper/paper.qmd
Update paper.qmd write more about Data section

@@
 
+The data on the trend in US anxiety and depressive disorder rates, measured as ~ from 2020 to 2024, was sourced from the Centers for Disease Control and Prevention (CDC).
+Alongside with National Estimate in which covers the whole population, trends in anxiety and depressive disorder rates by population subgroup, specifically categorized by age, race and ethnicity, sex, education groups were gathered from the National Center for Health Statistics (NCHS).
+The data is freely available at https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data, with raw files located in the inputs/data on the GitHub repository.
+
 ## Features
+
+In this paper, data validation is conducted using an R script file named '03-test_data' to ensure the accuracy of the dataset obtained directly from the source.
+The paper utilizes both 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401' and 'Lack_of_Social_Connection' CSV files.
+Then by the characteristics of the group, the data sets are separately saved as 'Age_subgroup_trends' where it only saves the rows with 'By Age' under the 'Group' column.
+Similarly, 'Educ_subgroup_trends' are the dataset only with the rows 'By Education' under the 'Group' column to identify the patterns of each population subgroup with classification of highest educational attainment.
+All CSV files are saved as parquet file as Parquet's columnar storage format.
+As opposed to row-based formats like CSV or Excel, Parquet allows it to efficiently handle analytical queries by accessing only the necessary columns of data, which reduces storage reads, improves query performance, and lowers storage costs.
+
+The column 'Value' is used to denote the symptom rate on the y-axis. 
+Column 'Time Period End Date' is used to denote the range of the period, a date for the x-axis.
 

### 2024-04-12 outputs/paper/paper.qmd

@@
 These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020).
-While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the nuanced interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).
+While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).
 
@@
 from 2020 to 2024, followed by an examination of how these rates vary across different demographic groups.
-Subsequent sections delve into the statistical methods and results for each research question, culminating in a discussion that synthesizes the findings and explores their broader implications for mental health research and policy.
+Subsequent sections discuss the statistical methods and results for each research question.
+It opens up the findings and let the world explores their broader implications for mental health research and policy.
 The conclusion summarizes the key insights, acknowledges the limitations of the study, and suggests avenues for future research.
@@
 # Data {#sec-data}
-
+---- A thorough discussion of measurement, relating to the dataset, is provided in the data section. ----
 ## Methodology
 
+The U.S.
+Census Bureau, in collaboration with five federal agencies, launched the Household Pulse Survey to produce data on the social and economic impacts of Covid-19 on American households.
+The Household Pulse Survey was designed to gauge the impact of the pandemic on employment status, consumer spending, food security, housing, education disruptions, and dimensions of physical and mental wellness (National Center for Health Statistics, 2024).
 The data on the trend in US anxiety and depressive disorder rates, measured as ~ from 2020 to 2024, was sourced from the Centers for Disease Control and Prevention (CDC).
@@
 What is another thing that we learn about the world?
-What are some weaknesses of what was done? 
-What is left to learn or how should we proceed in the future?
 
@@
 
-The survey was designed to meet the goal of accurate and timely weekly estimates. Hence, it was conducted by an internet questionnaire, with invitations to participate sent by email and text message.
+-- What are some weaknesses of what was done? -- 
+The survey was designed to meet the goal of accurate and timely weekly estimates.
+Hence, it was conducted by an internet questionnaire, with invitations to participate sent by email and text message (National Center for Health Statistics, 2024).
+Internet questionnaires face several significant challenges.
+One of the primary concerns is self-selection bias, where the survey tends to attract respondents who are particularly interested in the topic, which can skew the results and limit their generalizability.
+Additionally, these surveys may not reach a diverse demographic due to varying levels of internet access across different population segments, thus excluding certain groups, such as older adults or lower-income individuals, and potentially leading to a lack of representativeness.
+Respondents might also misunderstand or misinterpret questions without the opportunity for real-time clarification, compromising the accuracy of the data collected.
+Privacy and security concerns are prevalent too, as individuals may be hesitant to share personal or sensitive information online for fear of data breaches or doubts about the survey platform's security measures.
+Lastly, the validity and honesty of responses are at risk; while the anonymity of online surveys can encourage candidness, it might also lead to less thoughtful or dishonest answers, affecting the reliability of the survey outcomes (Dillman, Smyth, & Christian, 2014; Morling, 2018).
 
 ## Future Research
+-- What is left to learn or how should we proceed in the future? --
+For future research, survey can further ask what are the factors that affect their mood.
 

### 2024-04-12 outputs/paper/paper.qmd
Update paper.qmd

@@
 
+Through this analysis, we aim to better understand contributing factors of mental wellness of the US population.
+Furthermore, we display possible correlation between factors and the mentall wellness states.
+
 # Data {#sec-data}
----- A thorough discussion of measurement, relating to the dataset, is provided in the data section. ----
+
 ## Methodology
@@
 The Household Pulse Survey was designed to gauge the impact of the pandemic on employment status, consumer spending, food security, housing, education disruptions, and dimensions of physical and mental wellness (National Center for Health Statistics, 2024).
-The data on the trend in US anxiety and depressive disorder rates, measured as ~ from 2020 to 2024, was sourced from the Centers for Disease Control and Prevention (CDC).
-Alongside with National Estimate in which covers the whole population, trends in anxiety and depressive disorder rates by population subgroup, specifically categorized by age, race and ethnicity, sex, education groups were gathered from the National Center for Health Statistics (NCHS).
+In the paper, we will focus on the impact of the pandemic on mental wellness by analysing the dataset of the indicators of anxiety or depression based on reported frequency of symptoms.
+The data on the trend in US anxiety and depressive disorder rates, measured from 2020 to 2024, was sourced from the Centers for Disease Control and Prevention (CDC).
+Alongside with 'National Estimate' group in which covers the whole population trends, trends in anxiety and depressive disorder rates by population subgroup, specifically categorized by age, race and ethnicity, sex, education groups were gathered from the National Center for Health Statistics (NCHS).
 The data is freely available at https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data, with raw files located in the inputs/data on the GitHub repository.
@@
 In this paper, data validation is conducted using an R script file named '03-test_data' to ensure the accuracy of the dataset obtained directly from the source.
-The paper utilizes both 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401' and 'Lack_of_Social_Connection' CSV files.
+The paper utilizes both 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_
+Last_7_Days_20240401' and 'Lack_of_Social_Connection' CSV files.
 Then by the characteristics of the group, the data sets are separately saved as 'Age_subgroup_trends' where it only saves the rows with 'By Age' under the 'Group' column.
 Similarly, 'Educ_subgroup_trends' are the dataset only with the rows 'By Education' under the 'Group' column to identify the patterns of each population subgroup with classification of highest educational attainment.
-All CSV files are saved as parquet file as Parquet's columnar storage format.
-As opposed to row-based formats like CSV or Excel, Parquet allows it to efficiently handle analytical queries by accessing only the necessary columns of data, which reduces storage reads, improves query performance, and lowers storage costs.
-
+All CSV files are saved as parquet file.
+Due to its functionality, as opposed to row-based formats like CSV or Excel, Parquet allows it to efficiently handle analytical queries by accessing only the necessary columns of data, which reduces storage reads, improves query performance, and lowers storage costs.
 The column 'Value' is used to denote the symptom rate on the y-axis.

### 2024-04-12 outputs/paper/paper.qmd
Update paper.qmd

@@
 Last_7_Days_20240401' and 'Lack_of_Social_Connection' CSV files.
-Then by the characteristics of the group, the data sets are separately saved as 'Age_subgroup_trends' where it only saves the rows with 'By Age' under the 'Group' column.
-Similarly, 'Educ_subgroup_trends' are the dataset only with the rows 'By Education' under the 'Group' column to identify the patterns of each population subgroup with classification of highest educational attainment.
+Then by the characteristics of the group, the data sets are separately saved as 'Age_subgroup_trends' where it only saves the rows with 'By Age' under the 'Group' column, irrespective of race and ethnicity.
+Similarly, 'Educ_subgroup_trends' are the dataset only with the rows 'By Education' under the 'Group' column to identify the patterns of each population subgroup with classification of highest educational attainment, regardless of race and ethnicity.
 All CSV files are saved as parquet file.
@@
 ## Trend in US Anxiety and Depressive Disorder Rates
+
+The @fig-andtrend-graph overall trend in US anxiety and depressive disorder rates fluctuate over time, with the highest rates recorded in the end of 2020 and the beginning of 2021 at an average rate above 40% symptom rates for both anxiety disorder or depressive disorder.
+Subsequently, symptoms of anxiety disorder followed by the second showing similar trends as the first.
+Lastly, symptoms of depressive disorder show the relatively lower rates.
++ add more.
 
@@
 ```
-
-Both Anxiety and Depressive Disorder showing the similar trends over the period.
 
@@
 
+Both Anxiety and Depressive Disorder showing the similar trends over the period. From this, we can tell either the number of participants ~
+
 ## Ethical Implication

### 2024-04-12 outputs/paper/paper.qmd
Update paper.qmd

@@
 Subsequently, symptoms of anxiety disorder followed by the second showing similar trends as the first.
-Lastly, symptoms of depressive disorder show the relatively lower rates.
+Lastly, symptoms of depressive disorder show the relativelys lower rates.
 + add more.
+
+## Trend in US Anxiety and Depressive Disorder Rates
+
+The overall trend in US anxiety and depressive disorder rates shows significant fluctuations, with several notable peaks indicating heightened rates of reported symptoms.
+For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
+This peak reflects a substantial increase compared to earlier periods.
+Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increase in symptoms among the population.
+
+These peaks are interspersed with valleys, such as in late 2020, where rates temporarily dip to around 25%, showing the episodic nature of these conditions.
+The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctuation but maintaining relatively high levels overall.
+
+The data indicates that the combined symptom rates of both anxiety and depressive disorders generally present higher values, consistently staying above 30% after the initial 2020 data points.
+This trend underscores the overlapping nature of these mental health issues and their persistent impact on the US population.
+
+The graph, depicted as @fig-andtrend-graph, provides a line graph visualization of these rates over time.
+This visual representation allows for clear observation of trends and seasonal variations, with specific dates marked on the x-axis to aid in pinpointing changes.
+For example, a significant increase is noted as we move from late 2020 into early 2021, correlating with various global and national events that may have influenced mental health.
+
+## Trends in Depressive Disorder Rates by Population Subgroup by Age
+
+This analysis highlights the variations in depressive disorder rates across different age subgroups in the US, utilizing data up to early 2024.
+The visualization provided in the graph titled @fig-ageandtrend-graph reveals distinct temporal trends across various age demographics, effectively illustrating how depressive symptoms fluctuate over time among these groups.
+
+### Data Handling and Visualization Techniques
+The data is sourced from a Parquet file, ensuring robust and efficient handling of large datasets.
+For accuracy in temporal analyses, the 'Date' column is meticulously converted to a date format.
+The script focuses on depressive symptoms by age subgroup, filtering the data to showcase how these rates vary across different age demographics.
+A line graph, enhanced with different colors for each age group, facilitates easy tracking of each subgroup's symptom rates over time.
+
+### Annotation and Aesthetic Customization
+On January 10, 2022, the graph incorporates annotations for each age group, pinpointing the rates of depressive symptoms at this specific date.
+These annotations are strategically placed using `geom_text_repel` to prevent overlap, ensuring clarity and readability.
+The graph is further refined with horizontal lines at regular 10% intervals from 0 to 50%, providing a scale to assess the symptom rates.
+Custom dates along the x-axis highlight key moments in the timeline, aiding in the analysis of changes over time.
+
+### Thematic and Stylistic Elements
+The plot employs a classic theme with tailored font settings, which not only enhances the visual appeal but also ensures the readability of textual elements.
+The absence of a legend, dictated by the plot's customization, focuses attention on the lines themselves, each representing a different age group’s trend.
 

### 2024-04-12 outputs/paper/paper.qmd
Update paper.qmd

--- 2024-04-12 outputs/paper/paper.qmd
@@
 The @fig-andtrend-graph overall trend in US anxiety and depressive disorder rates fluctuate over time, with the highest rates recorded in the end of 2020 and the beginning of 2021 at an average rate above 40% symptom rates for both anxiety disorder or depressive disorder.
-Subsequently, symptoms of anxiety disorder followed by the second showing similar trends as the first.
-Lastly, symptoms of depressive disorder show the relatively lower rates.
-+ add more.
+Subsequently, symptoms of anxiety disorder showing similar trends with about 10% gap in-between.
+Lastly, the symptoms of depressive disorder followed by the anxiety disorder records the lowest out of three indicators, with an average of 23% symptom rates over the period.
+
+The overall trend in US anxiety and depressive disorder rates shows significant fluctuations, with several notable peaks indicating heightened rates of reported symptoms.
+For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
+This peak reflects a substantial increase compared to earlier periods.
+Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increase in symptoms among the population.
+
+These peaks are interspersed with valleys, such as in late 2020, where rates temporarily dip to around 25%, showing the episodic nature of these conditions.
+The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctuation but maintaining relatively high levels overall.
+
+The data indicates that the combined symptom rates of both anxiety and depressive disorders generally present higher values, consistently staying above 30% after the initial 2020 data points.
+This trend underscores the overlapping nature of these mental health issues and their persistent impact on the US population.
+
+The graph, depicted as @fig-andtrend-graph, provides a line graph visualization of these rates over time.
+This visual representation allows for clear observation of trends and seasonal variations, with specific dates marked on the x-axis to aid in pinpointing changes.
+For example, a significant increase is noted as we move from late 2020 into early 2021, correlating with various global and national events that may have influenced mental health.
 
@@
 ### Population subgroup by age
+
+@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
+This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
+
+### Analysis of Trends by Age Group
+The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
+
+1.
+**Young Adults (18-29 years):** This group shows relatively higher rates of depressive symptoms throughout the period, with peaks that suggest increased vulnerability during certain times.
+Notable spikes might correlate with specific events or seasons, indicating external impacts on mental health.
+
+2.
+**Middle-aged Groups (30-49 years):** These lines show moderate fluctuation but generally less variance compared to younger adults.
+This could indicate a more stable life situation or better coping mechanisms but still reflects noticeable impacts from external factors.
+
+3. **Older Adults (50 years and above):** Initially, older adults show lower rates of depressive symptoms. However, there is a trend of increasing rates as the period progresses.
 
@@
 
+## Trends in Depressive Disorder Rates by Population Subgroup by Sex
+
+@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:
+
+Female Subgroup: This line consistently shows higher rates of depressive symptoms compared to the male subgroup.
+The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms.
+The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.
+
+Male Subgroup: Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.
+
 ### Population subgroup by sex
@@
   aes(label = Subgroup),
-  nudge_x = 0,  # Adjust nudge_x and nudge_y to correctly position the labels
+  nudge_x = 0,  
   nudge_y = 0,
@@
 ```
+
+## Trends in Depressive Disorder Rates by Population Subgroup by Race and Ethnicity
+
+The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races).
+Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.
+
+Hispanic and African American Subgroups: These lines indicate relatively higher rates of depressive symptoms compared to other groups.
+
+Caucasian Subgroup: This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.
+
+Asian Subgroup: Typically, this line shows the lowest symptom rates among the subgroups.
+
+Other (Non-Hispanic, Other Races and Multiple Races): This category shows a unique trend with variability.
 
@@
 ```
+
+## Trends in Depressive Disorder Rates by Population Subgroup by Education
+
+This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
+The visualization provided in the @fig-educationandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
+
+Detailed Analysis of Trends by Education Level
+@fig-educandtrend-graph presents the depressive disorder rates for several educational subgroups, including those with a college degree or higher, some college or an associate's degree, a high school diploma or GED, and less than a high school diploma.
+Each line represents the trend within a specific educational subgroup, offering a visual representation of how mental health issues vary based on educational attainment.
+
+College Graduate or Higher: This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.
+
+Some College/Associate's Degree: Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups.
+This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.
+
+High School Diploma or GED: This subgroup shows higher rates of depressive symptoms compared to those with more education.
+The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.
+
+Less Than a High School Diploma: This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities.
+Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.
 
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+### Discussion of Results
+@fig-ageandtrend-graph indicates that while all age groups experienced fluctuations in depressive disorder rates, younger adults consistently reported higher rates.
+This could be due to a variety of factors including economic instability, career pressures, or social isolation, particularly accentuated by the pandemic.
+Trends of older adults, age 50 or more, might reflect accumulating stresses or health-related issues as they age, especially during challenging times like the pandemic.
+The peaks and valleys in the @fig-ageandtrend-graph correlate with the unfolding of global events, particularly the COVID-19 pandemic, which has been a significant stressor impacting mental health across all demographics.
+The data shows how these impacts vary significantly with age, suggesting that age-specific interventions might be necessary to address the mental health needs of different populations effectively.
 
-Both Anxiety and Depressive Disorder showing the similar trends over the period. From this, we can tell either the number of participants ~
+@fig-sexandtrend-graph suggests that both subgroups follow fairly similar trends over time, with both lines rising and falling in tandem.
+However, the female population consistently reports higher symptom rates than the male population.
+This persistent disparity can be indicative of the different ways in which depressive disorders manifest and are reported across genders, possibly influenced by societal roles, expectations, and differing stressors.
+
+African American and Hispanic group, Peaks within these subgroups from @fig-raceandtrend-graph might correspond to specific social or economic stressors that disproportionately affect these communities.
+Caucasian group, The graph points to underlying factors that may influence mental health across different community settings.
+
+Trends of the other group might reflect the diverse socio-economic and cultural backgrounds within this subgroup.
+
+Discussion of Results of the education subgroup
+The trends across educational subgroups underscore the strong correlation between educational attainment and mental health outcomes.
+Higher education often provides better opportunities for employment and income, which are crucial determinants of mental health.
+Conversely, lower educational attainment is closely associated with various life stressors that exacerbate mental health issues.
 
 ## Ethical Implication
+
+____
+### Implications
+The data underscores the need for targeted mental health services and interventions that cater specifically to the unique needs of different age groups.
+Understanding these trends helps in planning public health strategies and allocating resources more effectively to manage and mitigate depressive disorders among the population.
+
+In conclusion, the depressive disorder rates among different age groups provide crucial insights into the mental health landscape during and following significant global crises.
+These trends highlight the importance of continuous monitoring and responsive public health strategies to support mental wellness across the lifespan.
+
+The depressive disorder rates among different educational groups emphasize the need for policy interventions that consider the intersection of education, economic stability, and mental health.
+Tailoring mental health services to meet the needs of people across different educational backgrounds can lead to more effective prevention and treatment strategies, ultimately reducing the overall burden of depressive disorders in society.
+____
 

### 2024-04-13 outputs/paper/paper.qmd
Update paper.qmd

@@
 
-The @fig-andtrend-graph overall trend in US anxiety and depressive disorder rates fluctuate over time, with the highest rates recorded in the end of 2020 and the beginning of 2021 at an average rate above 40% symptom rates for both anxiety disorder or depressive disorder.
-Subsequently, symptoms of anxiety disorder showing similar trends with about 10% gap in-between.
-Lastly, the symptoms of depressive disorder followed by the anxiety disorder records the lowest out of three indicators, with an average of 23% symptom rates over the period.
-
-The overall trend in US anxiety and depressive disorder rates shows significant fluctuations, with several notable peaks indicating heightened rates of reported symptoms.
-For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
-This peak reflects a substantial increase compared to earlier periods.
-Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increase in symptoms among the population.
-
-These peaks are interspersed with valleys, such as in late 2020, where rates temporarily dip to around 25%, showing the episodic nature of these conditions.
-The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctuation but maintaining relatively high levels overall.
-
-The data indicates that the combined symptom rates of both anxiety and depressive disorders generally present higher values, consistently staying above 30% after the initial 2020 data points.
-This trend underscores the overlapping nature of these mental health issues and their persistent impact on the US population.
-
-The graph, depicted as @fig-andtrend-graph, provides a line graph visualization of these rates over time.
-This visual representation allows for clear observation of trends and seasonal variations, with specific dates marked on the x-axis to aid in pinpointing changes.
-For example, a significant increase is noted as we move from late 2020 into early 2021, correlating with various global and national events that may have influenced mental health.
-
 ```{r}
@@
 
+The @fig-andtrend-graph overall trend in US anxiety and depressive disorder rates fluctuate over time, with the highest rates recorded in the end of 2020 and the beginning of 2021 at an average rate above 40% symptom rates for both anxiety disorder or depressive disorder.
+Subsequently, symptoms of anxiety disorder showing similar trends with about 10% gap in-between.
+Lastly, the symptoms of depressive disorder followed by the anxiety disorder records the lowest out of three indicators, with an average of 23% symptom rates over the period.
+
+The overall trend in US anxiety and depressive disorder rates shows significant fluctuations, with several notable peaks indicating heightened rates of reported symptoms.
+For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
+This peak reflects a substantial increase compared to earlier periods.
+Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increase in symptoms among the population.
+
+These peaks are interspersed with valleys, such as in late 2020, where rates temporarily dip to around 25%, showing the episodic nature of these conditions.
+The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctuation but maintaining relatively high levels overall.
+
+The data indicates that the combined symptom rates of both anxiety and depressive disorders generally present higher values, consistently staying above 30% after the initial 2020 data points.
+This trend underscores the overlapping nature of these mental health issues and their persistent impact on the US population.
+
+The graph, depicted as @fig-andtrend-graph, provides a line graph visualization of these rates over time.
+This visual representation allows for clear observation of trends and seasonal variations, with specific dates marked on the x-axis to aid in pinpointing changes.
+For example, a significant increase is noted as we move from late 2020 into early 2021, correlating with various global and national events that may have influenced mental health.
+
 ## Trends in Depressive Disorder Rates by Population Subgroup
@@
 ### Population subgroup by age
-
-@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
-This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
-
-### Analysis of Trends by Age Group
-The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
-
-1.
-**Young Adults (18-29 years):** This group shows relatively higher rates of depressive symptoms throughout the period, with peaks that suggest increased vulnerability during certain times.
-Notable spikes might correlate with specific events or seasons, indicating external impacts on mental health.
-
-2.
-**Middle-aged Groups (30-49 years):** These lines show moderate fluctuation but generally less variance compared to younger adults.
-This could indicate a more stable life situation or better coping mechanisms but still reflects noticeable impacts from external factors.
-
-3. **Older Adults (50 years and above):** Initially, older adults show lower rates of depressive symptoms. However, there is a trend of increasing rates as the period progresses.
 
@@
 ```
+@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
+This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
+
+### Analysis of Trends by Age Group
+The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
+
+1.
+**Young Adults (18-29 years):** This group shows relatively higher rates of depressive symptoms throughout the period, with peaks that suggest increased vulnerability during certain times.
+Notable spikes might correlate with specific events or seasons, indicating external impacts on mental health.
+
+2.
+**Middle-aged Groups (30-49 years):** These lines show moderate fluctuation but generally less variance compared to younger adults.
+This could indicate a more stable life situation or better coping mechanisms but still reflects noticeable impacts from external factors.
+
+3. **Older Adults (50 years and above):** Initially, older adults show lower rates of depressive symptoms. However, there is a trend of increasing rates as the period progresses.
 
 ## Trends in Depressive Disorder Rates by Population Subgroup by Sex
-
-@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:
-
-Female Subgroup: This line consistently shows higher rates of depressive symptoms compared to the male subgroup.
-The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms.
-The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.
-
-Male Subgroup: Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.
 
@@
 ```
+@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:
+
+1.
+**Female Subgroup:** This line consistently shows higher rates of depressive symptoms compared to the male subgroup.
+The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms.
+The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.
+
+2.
+**Male Subgroup:** Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.
 
 ## Trends in Depressive Disorder Rates by Population Subgroup by Race and Ethnicity
-
-The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races).
-Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.
-
-Hispanic and African American Subgroups: These lines indicate relatively higher rates of depressive symptoms compared to other groups.
-
-Caucasian Subgroup: This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.
-
-Asian Subgroup: Typically, this line shows the lowest symptom rates among the subgroups.
-
-Other (Non-Hispanic, Other Races and Multiple Races): This category shows a unique trend with variability.
 
@@
 ```
+The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races).
+Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.
+
+1. **Hispanic and African American Subgroups:** These lines indicate relatively higher rates of depressive symptoms compared to other groups.
+
+2. **Caucasian Subgroup:** This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.
+
+3. **Asian Subgroup:** Typically, this line shows the lowest symptom rates among the subgroups.
+
+4. **Other (Non-Hispanic, Other Races and Multiple Races):** This category shows a unique trend with variability.
 
 ## Trends in Depressive Disorder Rates by Population Subgroup by Education
-
-This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
-The visualization provided in the @fig-educationandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
-
-Detailed Analysis of Trends by Education Level
-@fig-educandtrend-graph presents the depressive disorder rates for several educational subgroups, including those with a college degree or higher, some college or an associate's degree, a high school diploma or GED, and less than a high school diploma.
-Each line represents the trend within a specific educational subgroup, offering a visual representation of how mental health issues vary based on educational attainment.
-
-College Graduate or Higher: This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.
-
-Some College/Associate's Degree: Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups.
-This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.
-
-High School Diploma or GED: This subgroup shows higher rates of depressive symptoms compared to those with more education.
-The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.
-
-Less Than a High School Diploma: This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities.
-Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.
 
@@
 ```
+
+This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
+The visualization provided in the @fig-educationandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
+
+Detailed Analysis of Trends by Education Level
+@fig-educandtrend-graph presents the depressive disorder rates for several educational subgroups, including those with a college degree or higher, some college or an associate's degree, a high school diploma or GED, and less than a high school diploma.
+Each line represents the trend within a specific educational subgroup, offering a visual representation of how mental health issues vary based on educational attainment.
+
+1.
+**College Graduate or Higher:** This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.
+
+2.
+**Some College/Associate's Degree:** Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups.
+This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.
+
+3.
+**High School Diploma or GED:** This subgroup shows higher rates of depressive symptoms compared to those with more education.
+The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.
+
+4.
+**Less Than a High School Diploma:** This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities.
+Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.
+
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-alonetrend-graph
+#| fig-cap: "Adults who usually or always feel lonely"
 

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd
update paper

@@
 during and after the COVID-19 pandemic, analyzing data from 2020 to 2024.
-Using advanced statistical methods in R, it uncovered significant variations in mental health impacts across different demographic groups.
+Using statistical methods in R, it uncovered variations in mental health impacts across different demographic groups.
 The research reveals a complex relationship between socio-cultural factors and mental health, highlighting the increased vulnerability of certain populations during global crises.
@@
 Our analysis focuses on the correlation between the prevalence of anxiety or depressive disorders and socio-cultural factors such as age, sex, race/ethnicity, and education level during the pandemic and post pandemic years of 2020 to 2024.
-Specifically, the estimand of this study is the difference in the rates of symptoms of anxiety or depressive disorders across individuals, correlated with socio-cultural factors including age, sex, race/ethnicity, and education level.
+Specifically, the estimand of this study is the difference in the rates of symptom of depressive disorders across individuals, correlated with socio-cultural factors including age, sex, race/ethnicity, and education level.
 
@@
 
-* How do adepressive rates differ based on education level?
+* How do depressive rates differ based on education level?
 
@@
         legend.direction = "vertical",
+        legend.text = element_text(family = "Times"),
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
@@
 
-The @fig-andtrend-graph overall trend in US anxiety and depressive disorder rates fluctuate over time, with the highest rates recorded in the end of 2020 and the beginning of 2021 at an average rate above 40% symptom rates for both anxiety disorder or depressive disorder.
-Subsequently, symptoms of anxiety disorder showing similar trends with about 10% gap in-between.
-Lastly, the symptoms of depressive disorder followed by the anxiety disorder records the lowest out of three indicators, with an average of 23% symptom rates over the period.
+The overall trend in US anxiety and depressive disorder rates @fig-andtrend-graph shows significant fluctuations over the observed period, with several notable peaks indicating heightened rates of reported symptoms.
+For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
+This peak reflects a substantial increase compared to earlier peeriods.
+Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increases in symptoms among the population.
 
-The overall trend in US anxiety and depressive disorder rates shows significant fluctuations, with several notable peaks indicating heightened rates of reported symptoms.
-For instance, one of the highest peaks occurs in early 2021, where the rate of symptoms for combined anxiety and depressive disorders reaches approximately 45%.
-This peak reflects a substantial increase compared to earlier periods.
-Another significant peak, observed in mid-2022, sees rates approaching closer to 36-37%, illustrating another period of notable increase in symptoms among the population.
+These peaks are interspersed with valleys, such as in late 2020, where rates temporarily din to around 25%, demonstrating the episodic nature of these conditions.
+The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctutation but maintaining relatively high levels overall.
 
-These peaks are interspersed with valleys, such as in late 2020, where rates temporarily dip to around 25%, showing the episodic nature of these conditions.
-The plot also highlights a general trend of increasing rates from the onset of the data in 2020 through to peaks in 2021, followed by some fluctuation but maintaining relatively high levels overall.
+In late 2023, there is a notable decline in the symptom rates for both anxiety and depressive disorders, suggesting a potential easing of these mental health challenges or the effectiveness of interventions and strategies implemented over the period.
+This decrease is significant as it may indicate periods of relief amidst the prevailing trends of increasing disorder rates, which could be crucial for future public health planning and policymaking.
 
-The data indicates that the combined symptom rates of both anxiety and depressive disorders generally present higher values, consistently staying above 30% after the initial 2020 data points.
-This trend underscores the overlapping nature of these mental health issues and their persistent impact on the US population.
-
-The graph, depicted as @fig-andtrend-graph, provides a line graph visualization of these rates over time.
+The @fig-andtrend-graph provides a line graph visualization of these rates over time.
 This visual representation allows for clear observation of trends and seasonal variations, with specific dates marked on the x-axis to aid in pinpointing changes.
-For example, a significant increase is noted as we move from late 2020 into early 2021, correlating with various global and national events that may have influenced mental health.
 
@@
 This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
-
-### Analysis of Trends by Age Group
 The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
@@
 3. **Older Adults (50 years and above):** Initially, older adults show lower rates of depressive symptoms. However, there is a trend of increasing rates as the period progresses.
-
-## Trends in Depressive Disorder Rates by Population Subgroup by Sex
 
@@
 
-## Trends in Depressive Disorder Rates by Population Subgroup by Race and Ethnicity
+### Trends in Depressive Disorder Rates by Population Subgroup by Race and Ethnicity
 
@@
 
-## Trends in Depressive Disorder Rates by Population Subgroup by Education
+### Trends in Depressive Disorder Rates by Population Subgroup by Education
 

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd

@@
 Notable spikes might correlate with specific events or seasons, indicating external impacts on mental health.
+During the period, the symptom rates of this group are generally 10% higher than the second highest age group.
+Moreover, it is observed that there is 20% difference gap with the lowest symptom rates age group, 80 years and above.
 
 2.
-**Middle-aged Groups (30-49 years):** These lines show moderate fluctuation but generally less variance compared to younger adults.
-This could indicate a more stable life situation or better coping mechanisms but still reflects noticeable impacts from external factors.
+**Middle-aged Groups (40-59 years):**This line show moderate fluctuation but generally less variance compared to younger adults or older adults.
+Middle-aged groups generally locate in between 30 -39 years young adult group and 60 - 69 years old adults group.
+However, on 2023 May, middle-aged group 40 - 49 years exceeds 30 - 39 years young adults group by a few percentage of symptom rates.
+Overall, both 40 - 49 years age group and 50 - 59 years age group demonstrate similar trends with some points where symptom rates of 50 - 59 years age group surpassed 40 - 49 years age group.
+For instance, 2021 March and 2022 September.
 
-3. **Older Adults (50 years and above):** Initially, older adults show lower rates of depressive symptoms. However, there is a trend of increasing rates as the period progresses.
+3.
+**Old Adults (80 years and above):** Most fluctuating age groups, with a peak in 2021 January and multiple lowest peaks including 2021 July, 2022 March, and 2022 August.
+This group still score below than majority of the age groups but
 

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd

@@
 ```
+
+Overall, the younger the age group is, the higher the symptom rates are.
+
 @fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
@@
 **Old Adults (80 years and above):** Most fluctuating age groups, with a peak in 2021 January and multiple lowest peaks including 2021 July, 2022 March, and 2022 August.
-This group still score below than majority of the age groups but
+This group still score below than majority of the age groups but there are several moments where it overtakes the symptom rates of 70 - 79 years old group.
 
@@
 **Female Subgroup:** This line consistently shows higher rates of depressive symptoms compared to the male subgroup.
-The trend line for females exhibits several pronounced peaks which suggest periods of increased stress or exacerbation of symptoms.
-The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.
+The trend line for females exhibits several pronounced peaks.
+Two major peaks happened in 2020 August and 2021 January.
+And then as of January 2021 the trends starting to decline up until June 2021.
+From there the trends are following sideways trends with minor peaks and troughs along the way until the end of 2023.
 
@@
 **Male Subgroup:** Although the rates for the male subgroup are generally lower than those for females, the trend line still shows significant fluctuation with similar peaks and troughs, indicating that males are also significantly affected by the same factors that increase depressive symptoms.
+Reaching the end of 2023, the line graphs for both population subgroups almost align with each other and exhibits almost identical behaviours.
 
@@
 This persistent disparity can be indicative of the different ways in which depressive disorders manifest and are reported across genders, possibly influenced by societal roles, expectations, and differing stressors.
+Higher trends of female group suggests periods of increased stress or exacerbation of symptoms.
+The higher overall symptom rates in this subgroup might reflect the broader social, economic, and perhaps biological factors that influence mental health disparities between sexes.
 

### 2024-04-14 outputs/paper/paper.qmd
commit

--- 2024-04-14 outputs/paper/paper.qmd
@@
 library(here)
-library(ggrepel)
 library(extrafont)
@@
 
-# Filter the data to get the rows for the specific date to label
-label_date <- as.Date("2022-01-10")
-label_data <- data %>%
-  filter(Date == label_date)
-
 # Plotting the line graph
@@
   geom_line() +
-  geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  family = "Times", color = "black",
-                  size = 3,  # Smaller text size
-                  arrow = arrow(type = "closed", length = unit(0.02, "inches"), angle = 15),
-                  box.padding = unit(0.5, "lines"),
-                  point.padding = unit(0.5, "lines")) +
   geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
@@
         axis.title.y = element_text(family = "Times"),
-        legend.position = "none",
+        legend.position = "bottom",  # Display legend at the bottom of the plot
+        legend.title = element_blank(),  # Remove the legend title if desired
+        legend.box = "horizontal",  # Arrange legend items horizontally
         plot.margin = unit(c(1, 1, 1, 1), "cm"))
@@
 ```
+
 @fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
@@
   geom_text_repel(data = label_data, aes(label = Subgroup, x = Date, y = Value), 
-                  nudge_x = 0, nudge_y = 0, family = "Times", color = "black",
+                  nudge_x = 0, nudge_y = 0, family = "Times",
                   size = 3,  # Make label text smaller
@@
 ```
+
 The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races).

### 2024-04-14 outputs/paper/paper.qmd
commit

@@
 
+Overall, the younger the age group is, the higher the symptom rates are.
 @fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd
race group 1.

@@
 
-The line graph in @fig-raceandtrend-graph shows the depressive disorder rates for several race and ethnicity subgroups, including Hispanic, Caucasian, African American, Asian, and Other (Non-Hispanic, other races and multiple races).
-Each line represents the trend within a specific subgroup, providing a visual representation of how symptom rates have evolved over the specified period.
+The analysis of depressive disorder rates among various racial and ethnic groups @fig-raceandtrend-graph reveals distinct patterns of mental health disparities from 2020 to 2024.
+The data, visualized through a line graph, indicates varying symptom rates across five subgroups: Hispanic, Caucasian, African American, Asian, and Other.
 
-1. **Hispanic and African American Subgroups:** These lines indicate relatively higher rates of depressive symptoms compared to other groups.
+1.
+**Hispanic and African American Subgroups:** Both subgroups exhibit relatively higer rates od depressive symptoms throughout the observed period compared to other groups.
+This may suggest a greater impact of socio-economic and possibly systemic factors affecting these communities disproportionately.
+The maximum rates observed for Hispanis and African Americans were 41.10% and 41.43%, respectively, with Hispanics showing a minimum rate significantly lower at 18.77%, suggesting more substantial fluctuatinos.
 
@@
 This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
-The visualization provided in the @fig-educationandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
+The visualization provided in the @fig-educandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
 

### 2024-04-14 outputs/paper/paper.qmd
Update paper.qmd

@@
 1.
-**Hispanic and African American Subgroups:** Both subgroups exhibit relatively higer rates od depressive symptoms throughout the observed period compared to other groups.
+**Hispanic and African American Subgroups:** Both subgroups exhibit relatively higer rates of depressive symptoms throughout the observed period compared to other groups.
 This may suggest a greater impact of socio-economic and possibly systemic factors affecting these communities disproportionately.
-The maximum rates observed for Hispanis and African Americans were 41.10% and 41.43%, respectively, with Hispanics showing a minimum rate significantly lower at 18.77%, suggesting more substantial fluctuatinos.
+The maximum rates observed for Hispanics and African Americans were 41.10% and 41.43%, respectively, with Hispanics showing a minimum rate significantly lower at 18.77%, suggesting more substantial fluctuatinos.
 
-2. **Caucasian Subgroup:** This group generally shows lower symptom rates than the Hispanic and African American subgroups but follows a similar trend of fluctuations.
+2.
+**Caucasian Subgroup:** While the Caucasian group shows lower symptom rates than the Hispanic and African American groups, it follows a similar pattern of fluctuations over time.
+The maximum rate for Caucasians was 35.17%, with an average rate of 27.92%, indicating that while the intensity may vary, the underlying factors influencing depressive symptoms are somewhat consistent across these groups.
 
-3. **Asian Subgroup:** Typically, this line shows the lowest symptom rates among the subgroups.
+3.
+**Asian Subgroup:** This group consistently shows the lowest symptom rates among the compared groups, with a maximum rate of 35.27% and a remarkably low minimum of 10.67%.
+The average rate stands at 22.74%, reflecting cultural, social, or possibly systemic differences in how mental health issues are reported, treated, or perceived within this community.
 
-4. **Other (Non-Hispanic, Other Races and Multiple Races):** This category shows a unique trend with variability.
+4.
+**Other (Non-Hispanic, Other Races and Multiple Races):** This category presents a unique trend line with variable rates, which could be indicative of the heterogeneous nature of this group.
+The highest recorded was 46.07%, and the lowest was 24.23%, with an average of 37.89%, suggesting significant variability possibly stemming from the diverse socio-economic and cultural backgrounds represented within this subgroup.
 
@@
 
-Detailed Analysis of Trends by Education Level
 @fig-educandtrend-graph presents the depressive disorder rates for several educational subgroups, including those with a college degree or higher, some college or an associate's degree, a high school diploma or GED, and less than a high school diploma.
@@
 
-1.
-**College Graduate or Higher:** This subgroup typically shows the lowest rates of depressive symptoms, which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.
+1. **Less Than a High School Diploma:** Individuals with less than an high school diploma experienced the highest depressive disorder rates throughout the period, with peaks reaching nearly 47%.
 
@@
 **Some College/Associate's Degree:** Individuals in this group exhibit slightly higher rates than those with higher education but still lower than the less educated groups.
-This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.
+This group also showed a maximum rate close to 40%, averaging 26 - 27% rates.
 
 3.
-**High School Diploma or GED:** This subgroup shows higher rates of depressive symptoms compared to those with more education.
-The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.
+**High School Diploma or GED:** For individuals holding a high school diploma or GED, the depressive rates were slightly lower but still significant, peaking at nearly 39%.
+It is showing similar pattern with **Some College/Associate's Degree** subgroups.
 
 4.
-**Less Than a High School Diploma:** This group consistently shows the highest rates of depressive symptoms, indicating significant vulnerabilities.
-Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.
+**College Graduate or Higher:** This subgroup typically shows the lowest rates of depressive symptoms.
+The Bachelor's degree or higher subgroup exhibited the lowest rates across all metrics, with a peak rate of just over 31% generally averaging 15% during the period.
 
@@
 
-What is done in this paper? 
-What is something that we learn about the world? 
-What is another thing that we learn about the world?
-
 ## Findings
@@
 
-African American and Hispanic group, Peaks within these subgroups from @fig-raceandtrend-graph might correspond to specific social or economic stressors that disproportionately affect these communities.
-Caucasian group, The graph points to underlying factors that may influence mental health across different community settings.
-
+Overall, the trends in depressive disorder rates by race and ethnicity @fig-raceandtrend-graph  underscore disparities in mental health experiences among different racial and ethnic groups in the U.S.
 Trends of the other group might reflect the diverse socio-economic and cultural backgrounds within this subgroup.
+These differences likely stem from a complex interplay of socio-economic factors, access to mental health services, cultural perceptions of mental health, and possibly systemic inequalities.
+The quantitative findings of maximum, minimum, and average rates for each subgroup add depth to our understanding of these disparities, highlighting the specific challenges and variabilities within each community.
 
 Discussion of Results of the education subgroup
+
+Factors such as lower economic stability, limited access to healthcare, and higher life stressors likely contribute to these higher rates.
+This group's high average rate suggests a consistent burden of depressive symptoms, potentially exacerbated by factors such as economic insecurity and limited access to mental health resources.
+
+Those with some college or an Associate's degree also showed high variability in depressive disorder rates indicating that even some post-secondary education does not fully mitigate the risk of higher depressive symptoms.
+This might reflect a mid-level access to resources and varying levels of stress related to educational and career expectations.
+
+High school diploma or GED, The increased rates could be linked to economic challenges, job market limitations, or the stress associated with lower social mobility.
+This reflects moderate but considerable mental health challenges within this educational subgroup.
+
+Bachelor's degree or higher subgroup which might indicate better access to resources, stronger economic stability, or higher awareness and utilization of mental health services.
+
 The trends across educational subgroups underscore the strong correlation between educational attainment and mental health outcomes.

### 2024-04-15 outputs/paper/paper.qmd
commit

@@
 ```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| label: fig-alonetrend-graph
-#| fig-cap: "Adults who usually or always feel lonely"
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(readr)
 
-# Define the path to the data file and load it
-social_data <- read_parquet(file = here::here("outputs/data/Social_Connection.parquet"))
+# Load the data
+data <- read_parquet(file = here::here("outputs/data/Social_Connection.parquet"))
 
-# Filter data for the indicator "Adults who usually or always feel lonely" and "By Age" subgroup
-social_age_data <- social_data %>%
-  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Age")
+# Filter data for the specific indicator
+lonely_data <- data %>%
+  filter(Indicator == "Adults who usually or always feel lonely")
 
-# Plot the stacked bar chart
-graph_age <- ggplot(social_age_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
+# Function to create a plot for a given group with specified y-axis limits
+create_plot <- function(data, group_name, ymax) {
+  data_group <- data %>%
+    filter(Group == group_name) %>%
+    group_by(Time.Period.Label, Subgroup) %>%
+    summarise(Value = sum(Value), .groups = "drop") %>%
+    arrange(Time.Period.Label, Subgroup)
+
+  # Add cumulative sum of Value for label positioning
+  data_group <- data_group %>%
+    group_by(Time.Period.Label) %>%
+    mutate(label_pos = cumsum(Value) - 0.5 * Value,
+           segment_size = Value)
+
+  # Create the plot
+  plot <- ggplot(data_group, aes(x = Time.Period.Label, y = Value, fill = Subgroup)) +
     geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Adults who usually or always feel lonely - By Age",
-       x = NULL,
-       y = "Value") +
-  theme_minimal()
+    geom_text(aes(y = label_pos, label = ifelse(segment_size > 5, Subgroup, "")), 
+              position = position_stack(vjust = 0.5), 
+              color = "white", family = "Times", check_overlap = TRUE, 
+              size = ifelse(data_group$segment_size > 5, 3, 0)) +
+    labs(title = paste(group_name),
+         y = "Symptom rates (%)",
+         x = NULL) +
+    ylim(0, ymax) +
+    theme_minimal() +
+    theme(text = element_text(family = "Times"),
+          axis.text.x = element_text(hjust = 1, size = 10),
+          plot.title = element_text(size = 7),
+          legend.position = "none")
 
-# Filter data for the indicator "Adults who usually or always feel lonely" and "By Sex" subgroup
-social_sex_data <- social_data %>%
-  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Sex")
+  return(plot)
+}
 
-# Plot the stacked bar chart
-graph_sex <- ggplot(social_sex_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
-  geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Adults who usually or always feel lonely - By Sex",
-       x = NULL,
-       y = "Value") +
-  theme_minimal()
+# Create plots for each group with specific y-axis limits
+plot_age <- create_plot(lonely_data, "By Age", 100)
+plot_sex <- create_plot(lonely_data, "By Sex", 30) 
+plot_education <- create_plot(lonely_data, "By Education", 70)
+plot_race <- create_plot(lonely_data, "By Race/Hispanic ethnicity", 70)
 
-# Filter data for the indicator "Adults who usually or always feel lonely" and "By Race/Hispanic ethnicity" subgroup
-social_race_data <- social_data %>%
-  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Race/Hispanic ethnicity")
+# Arrange plots in a 2 x 2 grid
+grid_plots <- grid.arrange(plot_age, plot_sex, plot_education, plot_race, ncol = 2, nrow = 2)
 
-# Plot the stacked bar chart
-graph_race <- ggplot(social_race_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
-  geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Adults who usually or always feel lonely - By Race",
-       x = NULL,
-       y = "Value") +
-  theme_minimal()
-
-# Filter data for the indicator "Adults who usually or always feel lonely" and "By Education" subgroup
-social_educ_data <- social_data %>%
-  filter(Indicator == "Adults who usually or always feel lonely", Group == "By Education")
-
-# Plot the stacked bar chart
-graph_educ <- ggplot(social_educ_data, aes(x = `Time.Period`, y = Value, fill = Subgroup)) +
-  geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Adults who usually or always feel lonely - By Education",
-       x = NULL,
-       y = "Value") +
-  theme_minimal()
-
-# Arrange graphs in single pane
-grid.arrange(graph_age, graph_sex, graph_race, graph_educ, nrow = 2, ncol = 2)
+# Print the arranged plots
+print(grid_plots)
 
@@
 ## Model set-up
+\begin{align} 
+y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma)
+\end{align}
 
@@
 
-### Discussion of Results
 @fig-ageandtrend-graph indicates that while all age groups experienced fluctuations in depressive disorder rates, younger adults consistently reported higher rates.
@@
 
-____
-### Implications
 The data underscores the need for targeted mental health services and interventions that cater specifically to the unique needs of different age groups.
@@
 Tailoring mental health services to meet the needs of people across different educational backgrounds can lead to more effective prevention and treatment strategies, ultimately reducing the overall burden of depressive disorders in society.
-____
 

### 2024-04-16 outputs/paper/paper.qmd
commit add the second plots in pie chart

@@
 ```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-lonely-age-pie
+#| fig-cap: "Adults who usually or always feel lonely by Age"
+
 # Load necessary libraries
@@
 library(dplyr)
-library(gridExtra)
 library(readr)
+library(here)
 
@@
 
-# Filter data for the specific indicator
+# Filter data for the specific indicator and group
 lonely_data <- data %>%
-  filter(Indicator == "Adults who usually or always feel lonely")
+  filter(Indicator == "Adults who usually or always feel lonely") %>%
+  filter(Group == "By Age") %>%
+  group_by(Subgroup) %>%
+  summarise(Value = sum(Value), .groups = "drop")
 
-# Function to create a plot for a given group with specified y-axis limits
-create_plot <- function(data, group_name, ymax) {
-  data_group <- data %>%
-    filter(Group == group_name) %>%
-    group_by(Time.Period.Label, Subgroup) %>%
-    summarise(Value = sum(Value), .groups = "drop") %>%
-    arrange(Time.Period.Label, Subgroup)
+# Calculate percentages
+lonely_data$Percentage <- lonely_data$Value / sum(lonely_data$Value) * 100
 
-  # Add cumulative sum of Value for label positioning
-  data_group <- data_group %>%
-    group_by(Time.Period.Label) %>%
-    mutate(label_pos = cumsum(Value) - 0.5 * Value,
-           segment_size = Value)
+# Create the pie chart
+pie_chart <- ggplot(lonely_data, aes(x = "", y = Percentage, fill = Subgroup)) +
+  geom_bar(width = 1, stat = "identity") +
+  coord_polar(theta = "y") +
+  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5),
+            family = "Times", size = 4) +  # Set text font to Times and adjust size
+  labs(title = "Adults who usually or always feel lonely by Age",
+       x = NULL, y = NULL, fill = "Age Group") +
+  theme_void() +
+  theme(legend.position = "right",
+        text = element_text(family = "Times"),  # Apply Times font to all text elements
+        plot.title = element_text(size = 14))  # Customize plot title
 
-  # Create the plot
-  plot <- ggplot(data_group, aes(x = Time.Period.Label, y = Value, fill = Subgroup)) +
-    geom_bar(stat = "identity", position = "stack") +
-    geom_text(aes(y = label_pos, label = ifelse(segment_size > 5, Subgroup, "")), 
-              position = position_stack(vjust = 0.5), 
-              color = "white", family = "Times", check_overlap = TRUE, 
-              size = ifelse(data_group$segment_size > 5, 3, 0)) +
-    labs(title = paste(group_name),
-         y = "Symptom rates (%)",
-         x = NULL) +
-    ylim(0, ymax) +
-    theme_minimal() +
+# Print the pie chart
+print(pie_chart)
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-lonely-education-pie
+#| fig-cap: "Adults who usually or always feel lonely by Education"
+
+# Change filter to "By Education"
+lonely_data_education <- data %>%
+  filter(Indicator == "Adults who usually or always feel lonely") %>%
+  filter(Group == "By Education") %>%
+  group_by(Subgroup) %>%
+  summarise(Value = sum(Value), .groups = "drop")
+
+lonely_data_education$Percentage <- lonely_data_education$Value / sum(lonely_data_education$Value) * 100
+
+pie_chart_education <- ggplot(lonely_data_education, aes(x = "", y = Percentage, fill = Subgroup)) +
+  geom_bar(width = 1, stat = "identity") +
+  coord_polar(theta = "y") +
+  geom_text(aes(label = sprintf("%.1f%%", Percentage)), position = position_stack(vjust = 0.5),
+            family = "Times", size = 4) +
+  labs(title = "Adults who usually or always feel lonely by Education",
+       x = NULL, y = NULL, fill = "Education Level") +
+  theme_void() +
   theme(text = element_text(family = "Times"),
-          axis.text.x = element_text(hjust = 1, size = 10),
-          plot.title = element_text(size = 7),
-          legend.position = "none")
+        plot.title = element_text(size = 14))
 
-  return(plot)
-}
-
-# Create plots for each group with specific y-axis limits
-plot_age <- create_plot(lonely_data, "By Age", 100)
-plot_sex <- create_plot(lonely_data, "By Sex", 30) 
-plot_education <- create_plot(lonely_data, "By Education", 70)
-plot_race <- create_plot(lonely_data, "By Race/Hispanic ethnicity", 70)
-
-# Arrange plots in a 2 x 2 grid
-grid_plots <- grid.arrange(plot_age, plot_sex, plot_education, plot_race, ncol = 2, nrow = 2)
-
-# Print the arranged plots
-print(grid_plots)
+print(pie_chart_education)
 

### 2024-04-18 outputs/paper/paper.qmd
Update paper.qmd

@@
 during and after the COVID-19 pandemic, analyzing data from 2020 to 2024.
-Using statistical methods in R, it uncovered variations in mental health impacts across different demographic groups.
+It uncovered variations in mental health impacts across different demographic groups.
 The research reveals a complex relationship between socio-cultural factors and mental health, highlighting the increased vulnerability of certain populations during global crises.
@@
 Similarly, 'Educ_subgroup_trends' are the dataset only with the rows 'By Education' under the 'Group' column to identify the patterns of each population subgroup with classification of highest educational attainment, regardless of race and ethnicity.
-All CSV files are saved as parquet file.
-Due to its functionality, as opposed to row-based formats like CSV or Excel, Parquet allows it to efficiently handle analytical queries by accessing only the necessary columns of data, which reduces storage reads, improves query performance, and lowers storage costs.
 The column 'Value' is used to denote the symptom rate on the y-axis.
@@
 
--- What are some weaknesses of what was done? -- 
 The survey was designed to meet the goal of accurate and timely weekly estimates.
@@
 ## Future Research
--- What is left to learn or how should we proceed in the future? --
 For future research, survey can further ask what are the factors that affect their mood.

### 2024-04-19 outputs/paper/datasheet_template.qmd
Update datasheet_template.qmd

@@
 ---
-title: "Datasheet for 'A dataset'"
-subtitle: "My subtitle if needed"
+title: "Datasheet for 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401'"
 author: Chay Park
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder"
 date: "`r Sys.time()`"
@@
 1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
-    - The dataset was created to enable analysis of Australian politicians.
-We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
+    - The dataset was created to complement the ability of the federal statistical system to respond and provide relavant information about how emergent issues are impacting American households (National Center for Health Statistics, 2024).
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - TBD
+    - Data was provided by NCHS/DHIS and the owner of the dataset is NCHS.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - TBD
+    - Although there was not significant information specified about the funding, generally in addition to annual appropriations from Congress, NCHS receives additional resources in the form of reimbursables from other Federal agencies.
+NCHS is reimbursed by other agencies to add specific questions of interest to our surveys (National Center for Health Statistics, 2023).
 4. *Any other comments?*
-    - TBD
+    - Survey datas that are open to public is scarce and often not open to public. However, regarding health statistics for US research, NCHS is a good place to start with.
 
@@
 Please provide a description.*
-	- TBD
+	- Online questionnaire based survey with texts only.
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- TBD
+	- Just a single survey questionnaire.
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- TBD
+	- The dataset contain all possible instances, and yet considered a sample of instances from a larger set as it is still missing some responses from the whole population.
+The larger set would be a survey response from the whole population in US.
+The representativeness was verified as the hosting institution is the government associated.
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- TBD
+	- Raw data is nicely formatted in CSV form. Data types are among the following : 'Text', 'Floating Timestamp', and 'Number.' 
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- TBD
+	- Columns in this Dataset.
+(1) Indicator - Data Type [Text] (2) Group - Data Type [Text] (3) State - Data Type [Text] (4) Subgroup - Data Type [Text] (5) Phase - Data Type [Text] (6) Time Period - Data Type [Text] (7) Time Period Label - Data Type [Text] (8) Time Period Start Date - Data Type [Floating Timestamp] (9) Time Period End Date - Data Type [Floating Timestamp] (10) Value - Data Type [Number] (11) Low CI - Data Type [Number] (12) High CI - Data Type [Number] (13) Confidence Interval - Data Type [Text] (14) Quartile Range - Data Type [Text]
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- TBD
+	- Column 'Quartile Range' is missing for non-By State group. Only rows with 'By State' group has Quartile Range information.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- TBD
+	- The combination of Symptoms of Depressive Disorder and Symptoms of Anxiety Disorder are combined as Symptoms of Anxiety Disorder or Depressive Disorder. 
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- TBD
+	- No
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- TBD
+	- Not shown so far.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- TBD
+	- The dataset is self-contained.
 11.
@@
 If so, please provide a description.*
-	- TBD
+	- No
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- TBD
+	- Dataset could have been labeled White as Caucasian, Black as African American.
+Also, they are excluding the minorities by grouping them all as 'Non-Hispanic, other races and multiple races.' For instance, South Asian Americans, Middle Eastern Americans, Native Americans.
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- TBD
+	- By age, 18 - 29 years, 30 - 39 years, 40 - 49 years, 50 - 59 years, 60 - 69 years, 70 - 79 years, and 80 years and above. By sex, there are male and female.
 14.
@@
 If so, please describe how.*
-	- TBD
+	- No, each subgroup population is the accumulated, therefore it's hard to identify single individual.
 15.
@@
 If so, please provide a description.*
-	- TBD
-16. *Any other comments?*
-	- TBD
+	- The data reveals race, highest educational attainment, region (states), age.
 
@@
 # References
+
+@online{cdc_nchs_rate,
+    title = {Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days},
+    author = {National Center for Health Statistics},
+    year = {2024},
+    url = {https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data},
+    organization = {National Center for Health Statistics},
+    address = {United States},
+    note = {Accessed on April 1, 2024},
+}

### 2024-04-19 outputs/paper/datasheet_template.qmd
Update datasheet_template.qmd

@@
 Please provide a description.*
-	- Online questionnaire based survey with texts only.
+	- Each instance in the dataset represents a response to the Household Pulse Survey, reflecting individual experiences and assessments concerning various impacts of COVID-19.
+The instances include responses about mental health, economic status, and other personal impacts due to the pandemic.
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- Just a single survey questionnaire.
+	- The dataset is composed of multiple responses to the survey, each corresponding to an individual respondent.
+The total number of instances depends on the number of completed responses collected during the survey period.
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- The dataset contain all possible instances, and yet considered a sample of instances from a larger set as it is still missing some responses from the whole population.
-The larger set would be a survey response from the whole population in US.
-The representativeness was verified as the hosting institution is the government associated.
+	- The dataset is a sample from a larger set, which would be all eligible households in the U.S.
+The sampling strategy involved random selection from the Census Bureau's Master Address File, aiming to create a representative sample of the U.S.
+population by using demographic weighting and adjustment for nonresponse.
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- Raw data is nicely formatted in CSV form. Data types are among the following : 'Text', 'Floating Timestamp', and 'Number.' 
+	- Each instance consists of structed data collected via the survey.
+This includes both "raw" data in the form of survey responses and derived data such as timestamps and numerical values for responses.
+Each instance comprises responses to survey questions, which are formatted and categorized by various demographic and situational factors.
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- Columns in this Dataset.
-(1) Indicator - Data Type [Text] (2) Group - Data Type [Text] (3) State - Data Type [Text] (4) Subgroup - Data Type [Text] (5) Phase - Data Type [Text] (6) Time Period - Data Type [Text] (7) Time Period Label - Data Type [Text] (8) Time Period Start Date - Data Type [Floating Timestamp] (9) Time Period End Date - Data Type [Floating Timestamp] (10) Value - Data Type [Number] (11) Low CI - Data Type [Number] (12) High CI - Data Type [Number] (13) Confidence Interval - Data Type [Text] (14) Quartile Range - Data Type [Text]
+	- While not a label in the machine learning sense, each instance includes several attributes that categorize the data, such as indicators of mental health status, demographic groupings, and time-related information.
+These can be considered as labels for the purpose of analyzing survey data across different subgroups and times.
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- Column 'Quartile Range' is missing for non-By State group. Only rows with 'By State' group has Quartile Range information.
+	- Missing information occurs in instances where respondents did not answer all survey questions, or where certain data, such as the 'Quartile Range', is applicable only to specific subgroups.
+Reasons for missing data typically include nonresponse or the inapplicability of certain questions to all respondents.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- The combination of Symptoms of Depressive Disorder and Symptoms of Anxiety Disorder are combined as Symptoms of Anxiety Disorder or Depressive Disorder. 
+	- Relationships in the dataset are not about interactions between instances but rather about the correlations and trends that can be observed across different groups (e.g., demographic categories) or over time periods.
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- No
+	- The dataset does not specify recommended splits for training and testing as it is primarily designed for analysis and reporting rather than predictive modeling.
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- Not shown so far.
+	- As with any survey data, errors and noise can occur through misreporting or misunderstanding of survey questions by respondents.
+Redundancies might exist in the form of repeated demographic categorizations across multiple instances.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- The dataset is self-contained.
+	- Yes, the dataset is self-contained and does not rely on external resources. It provides all necessary information within the data itself.
 11.
@@
 If so, please provide a description.*
-	- No
+	- No, the dataset does not contain data considered confidential as personal identifiers are removed to ensure anonymity of the respondents.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- Dataset could have been labeled White as Caucasian, Black as African American.
-Also, they are excluding the minorities by grouping them all as 'Non-Hispanic, other races and multiple races.' For instance, South Asian Americans, Middle Eastern Americans, Native Americans.
+	- The dataset itself is not offensive; however, the content concerning individuals' mental health and economic impacts during the pandemic might be sensitive or cause discomfort due to the nature of the topics.
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- By age, 18 - 29 years, 30 - 39 years, 40 - 49 years, 50 - 59 years, 60 - 69 years, 70 - 79 years, and 80 years and above. By sex, there are male and female.
+	- Yes, the dataset identifies sub-populations by demographic attributes such as age and gender. These are clearly marked, allowing for detailed subgroup analysis within the dataset.
 14.
@@
 If so, please describe how.*
-	- No, each subgroup population is the accumulated, therefore it's hard to identify single individual.
+	- No, it is not possible to identify individuals directly from the dataset as the data is aggregated and anonymized, focusing on broader demographic and temporal trends.
 15.
@@
 If so, please provide a description.*
-	- The data reveals race, highest educational attainment, region (states), age.
+	- Yes, the dataset contains sensitive data related to race, age, and other demographic factors.
+However, the presentation of this data is in an aggregated form to prevent identification of individual respondents and ensure privacy and ethical compliance.
 
@@
 If so, please describe how.*
-	- TBD
+	- The data in the Household Pulse Survey was directly reported by subjects through an internet questionnaire.
+Given the nature of the survey, the responses were self-reported and not independently verified.
+However, the data has been weighted to adjust for nonresponse and to align with Census Bureau demographic estimates, which indirectly serves as a form of validation to ensure representativeness.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- The data was collected via an internet questionnaire, with invitations sent by email and text message.
+The Census Bureau and collaborating federal agencies likely validated the digital collection mechanism through pre-launch testing and quality assurance checks to ensure functionality and data integrity.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- The survey used a probabilistic sampling strategy where housing units from the Census Bureau's Master Address File Data were randomly selected.
+This approach ensures that the sample represents the general population.
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- The survey was conducted by the U.S.
+Census Bureau in collaboration with other federal agencies.
+Specific details on individual involvement and compensation are not typically disclosed in public documents, but governmnet employees would have conducted and managed the survey.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- The timeframe for data collection was during the COVID-19 pandemic, with the survey providing weekly estimates.
+The timeframe of data collection should match the creation timeframe of the data since the data relates to current experiences of households during the pandemic.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- Federal surveys often undergo ethical review processes to ensure compliance with standards and regulations, including privacy protections.
+Details of these processes for the Household Pulse Survey specifically would be documented by the Census Bureau and related agencies.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- The data was collected directly from individuals, not through third parties. Respondents provided information through the questionnaire based on personal and household experiences.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- Participants were likely notified about the data collection at the point of contact - either through the email or text message invitaion.
+This notification would include information about the purpose of the survey and its voluntary nature.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- Consent to participate in the survey was implied by the completion and submission of the online questionnaire. The invitation to participate likely included language regarding consent.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- As the data collection involves a one-time survey response, there typically isn't a mechanism to revoke consent post-submission, especially since the data is anonymized for analysis.
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- Given the scope and scale of federal surveys, an impact analysis, including considerations for data protection and potential effects on respondents, is likely conducted.
+Specific outcomes and details might be available through official documnetation or upon request from the Census Bureau.
 12. *Any other comments?*
-	- TBD
+	- These responses are inferred from standard practices for federal surveys like the Household Pulse Survey; specific details would be provided by the Census Bureau or in official survey documentation.
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Cleaning and Validation: The data collected through online surveys typically undergoes initial cleaning to remove any obviously erroneous entries (e.g., ages outside plausible human ranges, invalid characters in numeric fields).
+	- Processing of Missing Values: Missing data is a common issue in survey responses.
+Techniques such as imputation (replacing missing data with statistical estimates), or simply marking data as missing, may be used depending on the nature of the question and the analysis needs.
+For weighted surveys like this one, the adjustment for nonresponse is a crucial aspect of ensuring that the results are representative, even with missing data.
+	- Labeling of Categories: Questions with categorical responses (like "yes/no," "frequently/sometimes/never") are labeled for ease of analysis.
+This process involves coding textual responses into numeric codes that can be easily processed statistically.
+	- Discretization or Bucketing: For continuous variables or ordinal data with a wide range of responses, discretization or bucketing might be used.
+For example, age might be grouped into categories like 18-24, 25-34, etc., to facilitate analysis and ensure privacy.
+	- Weighting: As mentioned, the data is weighted to adjust for the probability of selection and nonresponse.
+Weighting ensures that the survey results are representative of the broader population according to key demographic variables like age, gender, race and ethnicity, and educational attainment.
+	- Anonymization: To protect respondents' privacy, personally identifiable information (PII) is removed or obscured.
+This includes any direct identifiers or combinations of variables that could potentially be used to re-identify individuals.
+	- Quality Assurance Checks: Repeated entries, consistency of responses across questions, and outlier checks are typical quality assurance measures in survey data processing.
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- On the GitHub repository, follow inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- None
 4. *Any other comments?*
-	- TBD
+	- Aforementioned steps are generally documented in the methodological reports associated with the survey, which might be accessible through the Census Bureau's website or directly within the docomentation of the survey dataset.
+For exact specifics, however, reviewing these official documnets or contacting the managing federal agency would be necessary.
 

### 2024-04-19 outputs/paper/datasheet_template.qmd
Update datasheet_template.qmd

@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- The Household Pulse Survey data has been widely used for tracking and analyzing the social and economic impacts of the COVID-19 pandemic.
+Researchers, policymakers, and public health officials have utilized the data to understand changes in employment, mental health, food security, and other areas affected by the pandemic.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- You can find studies and papers utilizing the Household Pulse Survey data through academic databases and resources such as Google Scholar.
+Additionally, the U.S.
+Census Bureau’s website often features publications and analysis derived from the data.
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- Beyond studying the impact of COVID-19, the dataset could be used for longitudinal studies on public health trends, economic analysis, and social science research.
+It can serve as a baseline for future crises management studies, or for comparative studies on how different demographics cope with societal stressors.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- Given the self-reported nature of the data, researchers should be cautious about biases inherent in self-report surveys, such as social desirability bias or recall bias.
+Additionally, because the dataset represents a specific period (COVID-19 pandemic), care should be taken when generalizing findings to other times or situations.
+Mitigating these risks involves robust statistical techniques, clear reporting of the survey’s scope and limitations, and, where possible, validation with other data sources.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
-6. *Any other comments?*
-	- TBD
+	- The dataset should not be used for predicting individual behaviors or outcomes due to its aggregated and anonymized nature.
+It is also not suitable for clinical or diagnostic purposes, as the data reflects self-reported indicators rather than medically verified conditions.
 
@@
 If so, please provide a description.*
-	- TBD
+	- The Household Pulse Survey data is publicly available through the U.S.
+Census Bureau and can be accessed by researchers, policymakers, and the general public, promoting transparency and accessibility.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- The dataset is available for download in various formats (such as CSV) from the Census Bureau’s website.
+It does not typically have a DOI as it is a governmental statistical data release rather than a publication in a scientific archive.
 3. *When will the dataset be distributed?*
-	- TBD
+	- The dataset is released in phases and updates, often aligned with survey waves. The Census Bureau’s website provides timelines and updates regarding data release schedules.
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- As a governmental dataset, the Household Pulse Survey data is typically in the public domain, but users are encouraged to cite the source appropriately.
+Specific terms of use can be found on the Census Bureau’s website.
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- There are no export controls or regulatory restrictions on the dataset, given its nature as publicly available governmental data.
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
+	- As the Household Pulse Survey data is collected and distributed by the U.S.
+Census Bureau, a federal agency, it is typically not subject to export controls or specific regulatory restrictions.
+The data is publicly available and designed to be accessible by the general public, researchers, and policymakers both domestically and internationally.
+This openness aligns with the mission of the Census Bureau to provide useful data to help government officials, businesses, and the public make informed decisions.
+However, users of the data should be aware of the general legal responsibilities that come with handling data, especially when used in research and publication.
+These responsibilities may include ensuring privacy protections and ethical use of the data, particularly when integrating this data with other datasets that might have their own restrictions or sensitive information.
 7. *Any other comments?*
-	- TBD
+	- For specific details about any applicable terms of use, users can refer to the Census Bureau’s website or the direct Household Pulse Survey page, which provide guidelines and updates on data usage, distribution, and any pertinent legal notices.
+These resources ensure users are fully informed of their rights and obligations when accessing and using the dataset.
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- The U.S. Census Bureau, along with collaborating federal agencies, is responsible for maintaining, updating, and hosting the dataset.
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- Contact Name	: National Center for Health Statistics and Contact Email	: cdcinfo@cdc.gov
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- The dataset is updated periodically with new survey waves. The Census Bureau communicates these updates through its website and via press releases to registered users and the public.
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- While specific retention limits are not typically imposed on public domain data like this, the data is managed in accordance with federal records management laws and guidelines.
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- Older versions of the Household Pulse Survey data are typically archived and remain accessible through the U.S.
+Census Bureau’s website.
+This ensures that historical data can be reviewed and utilized for longitudinal studies or comparative analyses.
+Each release is clearly dated and labeled, allowing researchers to access specific data waves or versions according to their needs.
+The Census Bureau typically does not remove older data versions but instead adds new survey data as additional files or entries within their data portal.
+In the event of any significant changes to the dataset or its availability, the Census Bureau communicates these updates through announcements on their website and potentially via email notifications to users who have registered for updates.
+Researchers and data users are encouraged to regularly check the Census Bureau’s website for the most current data and for any notices regarding updates or changes to the dataset’s maintenance and availability.
+This proactive approach helps ensure that all users have access to the latest information and data resources provided by the agency.
 7.
@@
 If so, please provide a description.*
-	- TBD
-8. *Any other comments?*
-	- TBD
+	- Generally, external contributions to governmental datasets like this are not standard practice.
+However, researchers can use the data to build secondary datasets or augment it with other data sources for specific studies, which they can then make available independently.
 

### 2024-04-19 outputs/paper/datasheet_template.qmd
Edit datasheet

@@
 ---
-title: "Datasheet for 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401'"
+title: "Datasheet for 'Anxiety_or_Depression'"
 author: Chay Park
 thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder"
-date: "`r Sys.time()`"
-date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+date: today
+date-format: long
+abstract: "The Household Pulse Survey, conducted by the U.S.
+Census Bureau in collaboration with several federal agencies, serves as a critical dataset to evaluate the socioeconomic and health impacts of the COVID-19 pandemic on American households.
+This dataset includes self-reported data collected through an internet questionnaire, focusing on areas such as mental health, economic status, and educational disruptions.
+The survey employs a probabilistic sampling strategy from the Census Bureau's Master Address File to ensure representativeness, with data being weighted according to demographic benchmarks.
+This datasheet provides detailed insights into the dataset’s composition, collection process, usage, distribution, and maintenance, offering essential information for researchers and policymakers utilizing this resource to understand and respond to the pandemic's effects."
 format: pdf
@@
 # References
-
-@online{cdc_nchs_rate,
-    title = {Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days},
-    author = {National Center for Health Statistics},
-    year = {2024},
-    url = {https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data},
-    organization = {National Center for Health Statistics},
-    address = {United States},
-    note = {Accessed on April 1, 2024},
-}

### 2024-04-19 outputs/paper/paper.qmd
update the format

@@
 
-* Is there codependency of social connection on one's depression level?
-
 Through this analysis, we aim to better understand contributing factors of mental wellness of the US population.
-Furthermore, we display possible correlation between factors and the mentall wellness states.
+Furthermore, we display possible correlation between factors and the mental wellness states.
 
@@
 
+Overall, the younger the age group is, the higher the symptom rates are.
+@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
+This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
+The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
+
 ```{r}
@@
 
-Overall, the younger the age group is, the higher the symptom rates are.
-@fig-ageandtrend-graph illustrates the trends in depressive disorder rates by population subgroup segmented by age, covering the period from May 2020 to March 2024.
-This graph reveals several key insights about how depressive symptoms have fluctuated across different age groups during and potentially influenced by the ongoing global and societal changes.
-The line graph distinguishes each age group with a separate line, showing the trend of depressive disorder rates for each demographic:
-
 1.
@@
 ### Population subgroup by sex
+
+@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:
 
@@
 ```
-@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:
 
@@
 ### Trends in Depressive Disorder Rates by Population Subgroup by Race and Ethnicity
+
+The analysis of depressive disorder rates among various racial and ethnic groups @fig-raceandtrend-graph reveals distinct patterns of mental health disparities from 2020 to 2024.
+The data, visualized through a line graph, indicates varying symptom rates across five subgroups: Hispanic, Caucasian, African American, Asian, and Other.
 
@@
 
-The analysis of depressive disorder rates among various racial and ethnic groups @fig-raceandtrend-graph reveals distinct patterns of mental health disparities from 2020 to 2024.
-The data, visualized through a line graph, indicates varying symptom rates across five subgroups: Hispanic, Caucasian, African American, Asian, and Other.
-
 1.
@@
 ### Trends in Depressive Disorder Rates by Population Subgroup by Education
+
+This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
+The visualization provided in the @fig-educandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
 
@@
 ```
-
-This analysis highlights the variations in depressive disorder rates across different educational subgroups in the US, utilizing data from mid 2020 up to early 2024.
-The visualization provided in the @fig-educandtrend-graph reveals distinct temporal trends across various education demographics, illustrating how depressive symptoms fluctuate over time among these groups.
 
@@
 ## Future Research
-For future research, survey can further ask what are the factors that affect their mood.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-## Diagnostics
+Given the self-reported nature of the data, researchers should be cautious about biases inherent in self-report surveys, such as social desirability bias or recall bias.
+Additionally, because the dataset represents a specific period (COVID-19 pandemic), care should be taken when generalizing findings to other times or situations.
+Mitigating these risks involves robust statistical techniques, clear reporting of the survey's scope and limitations, and, where possible, validation with other data sources.
+Furthermore, beyond studying the impact of COVID-19, the dataset could be used for longitudinal studies on public health trends, economic analysis, and social science research.
+It can serve as a baseline for future crises management studies, or for comparative studies on how different demographics cope with societal stressors.
 

### 2024-04-19 outputs/paper/paper.qmd
title and subtitle are renamed

@@
 ---
-title: "Are we living in a depressive society?"
-subtitle: "Trends in symptoms of depressive disorder in the US population from May 2020 to March 2024"
+title: "Socio-Cultural Influences on Depressive Disorders in the US: An Analysis from 2020 to 2024"
+subtitle: "Exploring the Impact of Age, Gender, Race, and Education on Mental Health Trends During and After the COVID-19 Pandemic"
 author: Chay Park
